---
title: "Cog_hydra_analysis_matched_imaging_and_non_imaging_n1424_k3, old hydra with new code from toni"
author: "Erica Baller"
date: "11/21/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 9)
library(visreg)
library(mgcv)
library(tableone)
library(dplyr)
library(plm)
library(MatchIt)
library(tidyr)
library(ggplot2)
library(reshape)
library(emmeans)
require(cowplot)
theme_update(plot.title = element_text(hjust = 0.5))
source("~/BBL/from_chead/ballerDepHeterogen/ballerDepHeterogenScripts/Hydra_functions.R")
```

## R Markdown

This script goes through demographics, cnb scores, health, and psych summaries, adds clustering information, runs statistics and makes graphs from results.

This script goes through demographics, clinical scores, health, and psych summaries, adds clustering information, runs statistics and makes graphs from results.

Part 1 : Read in csv.s
  -This script reads in demographics, cnb_scores, health and psych summaries, merges them, removes NAs, codes and separates by depression.

Part 2 : merge with hydra
  -It then merges these documents with hydra output (made in cbica), adding Hydra_k1 through Hydra_k10 columns (which represent the number of clusters)
  -The script reads in 3 different types of groups (matched)

Part 3 : Demographics tables
  - Demographics tables matched
  
Part 4 : Graphing
  - Graphs were then made.  
    *For continuous variables(age, medu1), the graphs represent means, with SEM as error bars
    *For categorical variables (race, sex) the graphs are percentages (caucasian, male) per group, with chisq used to calculate significance

Part 5 : LM/GAM/LM with Agesq
  -The script then runs LM on each cognitive score (cnb_measure ~ hydra_group). 
   - Does gam (cnb_measure ~ hydra_group + s(age) + sex)
   - Does LM with ageSq (cnb_measure ~ hydra_group + ageSq + sex )
  -There is a test option that does this for all CT measures and all hydra groups, but for the remainder of the analysis, Hydra_k3 was the only classification more deeply explored.

Part 6 : Anovas
  -Anovas were also run on the results of the LM of each cnb value by cluster.

Part 7 : FDR Correction
  -FDR correction was calculated for each cnb measure ANOVA output
  -A table of the results was extracted
 

```{r CNB, echo = FALSE}
#######################################################
############ READ IN, MERGE AND SUBSET DATA############
#######################################################

#set defaults:
num_clusters <- 3
cluster_titles <- get_cluster_titles(hydra_cluster = num_clusters)

#read in csvs
demographics <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/n9498_demographics_go1_20161212.csv", header = TRUE, sep = ",") #from /data/joy/BBL/projects/ballerDepHeterogen/data/n9498_demographics_go1_20161212.csv
cnb_scores <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/n9498_cnb_zscores_fr_20170202.csv", header = TRUE, sep = ",") 
health <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/n9498_health_20170405.csv", header = TRUE, sep = ",") #from /data/joy/BBL/projects/ballerDepHeterogen/data/n9498_health_20170405.csv
psych_summary <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/n9498_goassess_psych_summary_vars_20131014.csv", header = TRUE, sep = ",") #from /data/joy/BBL/projects/ballerDepHeterogen/data/n9498_goassess_psych_summary_vars_20131014.csv
cnb_factor_scores <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/n9498_cnb_factor_scores_fr_20170202.csv", header = TRUE, sep = ",")
extended_names <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/dictionaries/cnb_scores_and_names.csv", header = TRUE) #reads a 2 column table with mappings of cnb scores to actual names

#read in Hydra cluster data -> AG (all_gender), M(males), F(females) 
#hydra_AG_matched_clusters <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/hydra_output_from_cbica/hydra_matched/matched_imaging_plus_non_imaging/CogData_matched_age_and_sex_n1424_matched_imaging_plus_non_imaging_HydraSubtypes.csv", header = TRUE, sep = ",")

hydra_AG_matched_clusters <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/hydra_output_from_cbica/hydra_matched/20181121_OLD_HYDRA_with_new_script_from_toni/CogData_age_and_sex_n1424_matched_imaging_plus_non_imaging_replication_20181121_HydraSubtypes.csv", header = TRUE, sep = ",")

#Coerce hydra values into factor format
hydra_names <- names(hydra_AG_matched_clusters[2:11])
hydra_AG_matched_clusters[hydra_names] <- lapply(hydra_AG_matched_clusters[hydra_names], factor)


############
#prepping and merging big CNB and demographics stuff
############

#remove people with NA for race, age, or sex.  START WITH N = 9498
demographics_noNA_race <- demographics[!is.na(demographics$race),] #everyone has a race, N = 9498
demographics_noNA_race_age <- demographics_noNA_race[!is.na(demographics_noNA_race$ageAtClinicalAssess1),] # 86 people do not have age at clinical assessment.  N = 9412
demographics_noNA_race_age_sex <- demographics_noNA_race_age[!is.na(demographics_noNA_race_age$sex),] #everyone has a sex, N = 9412
demographics_noNA_race_age_andCNBage_sex <- demographics_noNA_race_age_sex[!is.na(demographics_noNA_race_age_sex$ageAtCnb1),] #6 people do not have ageAtCnb1, N = 9406

#remove people with NA for depression or total psych score, START WITH N = 9498
psych_summary_no_NA_dep <- psych_summary[!is.na(psych_summary$smry_dep),] #take out those with NA for depression, 87 people N = 9411
psych_summary_no_NA_dep_and_smry_psych_overall <- psych_summary_no_NA_dep[!is.na(psych_summary_no_NA_dep$smry_psych_overall_rtg),] #take out those with NA for overall psych rtg, no additional people lost, N = 9411

#merge demographics and cnb #this is if we want to include people without full demographic data
dem_cnb <- merge(demographics_noNA_race_age_andCNBage_sex, cnb_scores, by = "bblid") #merge demographics and cnb, N = 9406
psych_health <- merge(psych_summary_no_NA_dep_and_smry_psych_overall, health, by = "bblid") #merge psych and health, N = 9411
dem_cnb_psych_health_merged <- merge (dem_cnb, psych_health, by = "bblid") #merge all 4 csvs, lost 1 person [134716] (had demographics, but no psych ratings): N = 9405
dem_cnb_psych_health_factor_scores_merged <- merge(dem_cnb_psych_health_merged, cnb_factor_scores, by = "bblid")

#make subsets
subset_just_dep_and_no_medicalratingExclude <- subset.data.frame(dem_cnb_psych_health_factor_scores_merged, (medicalratingExclude == 0) & (smry_dep == 4), select = "bblid") #subset people who were not medically excluded and who are depressed, N = 776
subset_no_psych_no_medicalratingExclude <- subset.data.frame(dem_cnb_psych_health_factor_scores_merged, (medicalratingExclude == 0) & (smry_psych_overall_rtg < 4), select = "bblid") #subset people who are psychiatrically healthy, N = 2508
subset_dep_or_no_psych_and_no_medicalratingExclude <- subset.data.frame(dem_cnb_psych_health_factor_scores_merged, (medicalratingExclude == 0) & ((smry_dep == 4) | (smry_psych_overall_rtg <4))) #subset including both depressed and healthies, good for regressions, N = 3284

#would binarize depression smry score to -1 (less than 4, not depressed) and 1 (score 4 , depressed)
dep_binarized <- ifelse(subset_dep_or_no_psych_and_no_medicalratingExclude$smry_dep == 4, 1, -1)
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED <- cbind(subset_dep_or_no_psych_and_no_medicalratingExclude, dep_binarized) #N = 3284

#make depression and gender into factor scores
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$dep_binarized <- as.factor(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$dep_binarized)
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$sex <- as.factor(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$sex)

#divide ageAtCNB by 12 for age
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$age_in_years <- subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$ageAtCnb1/12

#race binarized for plotting purposes, caucasian 1, non-caucasion 0
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$race_binarized <- ifelse(as.factor(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$race) == 1, 1, 0)

#add age squared mean-centered term for use in LM
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$ageSq <- as.numeric(I(scale(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$age_in_years, scale = FALSE, center = TRUE)^2))

#remove people with NA in their cognitive measures
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED <- subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED[complete.cases(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED[14:39]),]

################################################
### Merge clustering data with subsetted data ##
################################################

#AG (all gender), M (males), F (females) 
#AG Matched - n 1424

subset_with_clusters_AG_matched <- merge(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED, hydra_AG_matched_clusters, by = "bblid")
clusters <- names(subset_with_clusters_AG_matched[grep ("Hydra", names(subset_with_clusters_AG_matched))])
summary_factor_scores <- names(subset_with_clusters_AG_matched[grep ("NAR_Overall", names(subset_with_clusters_AG_matched))])


```

##Demographics

```{r Demographics, echo = FALSE}
#############################
####### Demographics ########
#############################

#######Matched group all clusters ##############

make_demographics_table(data_frame = subset_with_clusters_AG_matched, hydra_cluster = num_clusters)


```
```{r graphs by cluster, echo = FALSE}


#######Chi-square for males/females and race########
##########By males, and by caucasians ##############

#Chi squared 
chisq_matched_sex <- chi_sq(data_frame = subset_with_clusters_AG_matched, "sex", num_clusters)
chisq_matched_race <- chi_sq(data_frame = subset_with_clusters_AG_matched, "race_binarized", num_clusters)

#get means/stds
total_people_Hydra <- total_people_per_cluster(data_frame = subset_with_clusters_AG_matched, hydra_cluster = num_clusters)

num_men_all_clusters <- total_people_per_cluster_by_group(data_frame = subset_with_clusters_AG_matched, variable = "sex", hydra_cluster = num_clusters, group_val = 1)
num_caucasian_all_clusters <- total_people_per_cluster_by_group(data_frame = subset_with_clusters_AG_matched, variable = "race_binarized", hydra_cluster = num_clusters, group_val = 1)

percent_men_all_clusters <- (num_men_all_clusters/total_people_Hydra) * 100
percent_caucasian_all_clusters <- (num_caucasian_all_clusters/total_people_Hydra)*100

p_values <- c("", chisq_matched_sex$p.value, "", chisq_matched_race$p.value)

dat_sex_race <- data.frame(cl = c(cluster_titles, "Significance"), 
                           num_males = c(num_men_all_clusters, "---"),
                           percent_males = round(c(percent_men_all_clusters, chisq_matched_sex$p.value), 2), 
                           num_caucasians = c(num_caucasian_all_clusters, "---"),
                           percent_caucasian = round(c(percent_caucasian_all_clusters, chisq_matched_race$p.value),2))
dat_sex_race_no_significance <-  data.frame(cl = cluster_titles, 
                                            num_males = (num_men_all_clusters),
                                            percent_males = percent_men_all_clusters, 
                                            num_caucasians = num_caucasian_all_clusters,
                                            percent_caucasian = percent_caucasian_all_clusters)                 
percentages <- data.frame(cl=cluster_titles, percent_males = percent_men_all_clusters, percent_caucasians = percent_caucasian_all_clusters)
percentages_for_plot <- melt(percentages, id.vars = "cl")
names(percentages_for_plot) <- c("cluster", "group", "percent")

#Set Titles for plots
title1 <- paste0("Hydra_k", num_clusters, " Percentages")

if(chisq_matched_sex$p.value < 0.05) {
  title2 <- paste0("Hydra_k", num_clusters, "% Male, p < 0.05")
} else {
  title2 <- paste0("Hydra_k", num_clusters, "% Male, p = ", round(chisq_matched_sex$p.value, 2))
}

if(chisq_matched_race$p.value < 0.05) {
  title3 <- paste0("Hydra_k", num_clusters, "% Caucasian, p < 0.05")
} else {
  title3 <- paste0("Hydra_k", num_clusters, "% Caucasian, p = ", round(chisq_matched_race$p.value, 2))
}

#plot
ggplot(data = percentages_for_plot, aes(x = group, y = percent, group = cluster)) + 
  geom_line(aes(color=cluster)) +
  geom_point(aes(color=cluster)) + 
  ggtitle(title1)

ggplot(dat_sex_race_no_significance, aes(x = cl, y = percent_males, fill=cl)) + geom_col() +
  scale_x_discrete(limits=cluster_titles) + ylim(0, 100) + xlab("Clusters") + ylab("% Male") + 
  ggtitle(title2) + scale_fill_discrete(breaks=cluster_titles) +
  guides(fill=guide_legend(title=NULL))

ggplot(dat_sex_race_no_significance, aes(x = cl, y = percent_caucasian, fill=cl)) + geom_col() + 
  scale_x_discrete(limits=cluster_titles) + ylim(0, 100) + xlab("Clusters") + ylab("% Caucasian") + 
  ggtitle(title3) + scale_fill_discrete(breaks=cluster_titles) + 
  guides(fill=guide_legend(title=NULL))


#ggplot(subset_with_clusters_AG_matched, aes(x=Hydra_k3, y = age_in_years, color = Hydra_k3, fill = Hydra_k3)) + 
 # geom_violin() +
  #xlab ("Clusters") + ylab("Age in Years") +
  #scale_x_discrete(limits=c("1", "2", "3", "-1"), labels=c("Cluster 1", "Cluster 2", "Cluster 3", "TD")) +
  #scale_color_hue(labels = c("Cluster 1", "Cluster 2", "Cluster 3", "TD")) + 
  #ylim(0, 30)
#############################
######### Bar Graphs ########
#############################

variable_name_string <- c("age", "medu") #this allows you to specify the actual titles, if different from the data frame titles
plot_list <- plot_continuous_variables(data_frame = subset_with_clusters_AG_matched, var1 = "age_in_years", var2 = "medu1", hydra_cluster = num_clusters, optional_variable_name_string = variable_name_string)
for(x in 1:length(plot_list)){
  print(plot_list[[x]])
}



```


```{r Stats, echo=FALSE}
#################################
# Linear Model for each measure #
##### Results stored in list ####
#################################

#get CNB measure names
cnb_measure_names <- names(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED)[grep("_z", names(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED))] #get the names of all the columns with _z in the name

cnb_speed_names <- cnb_measure_names[grep(pattern = "s_z", x = cnb_measure_names)]
cnb_accuracy_names <- cnb_measure_names[grep(pattern = "s_z", x = cnb_measure_names, invert = TRUE)]

cluster_names <- colnames(hydra_AG_matched_clusters[,2:11])

cnb_measure_names_list <- names(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED)[grep("_z", names(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED))] #get the names of all the columns with _z in the name
cluster_names_list <- colnames(hydra_AG_matched_clusters[,2:11])

#### All Hydra clusters in embedded lis t######
cnb_score_cluster_stats_lm_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
  cnb_score_cluster_stats_lm_AG_matched_withincluster<- lapply(cnb_measure_names_list, cluster=as.name(cluster_name), function(cnb_measure_name, cluster) 
  {
    cnb_measure <- as.name(cnb_measure_name)
    lm(substitute(cnb_measure ~ cluster, list(cnb_measure = cnb_measure, cluster = cluster)), data = subset_with_clusters_AG_matched)
  })
  setNames(cnb_score_cluster_stats_lm_AG_matched_withincluster, cnb_measure_names_list)
})

names(cnb_score_cluster_stats_lm_AG_matched_by_cluster_1through10) <- cluster_names_list


#gam
cnb_score_cluster_stats_gam_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
 cnb_score_cluster_stats_gam_AG_matched_withincluster<- lapply(cnb_measure_names_list, cluster=as.name(cluster_name),   function(cnb_measure_name, cluster) 
 {
    cnb_measure <- as.name(cnb_measure_name)
    gam(substitute(cnb_measure ~ cluster + sex + s(age_in_years), list(cnb_measure = cnb_measure, cluster = cluster)), data = subset_with_clusters_AG_matched, method="REML")
  })
 setNames(cnb_score_cluster_stats_gam_AG_matched_withincluster, cnb_measure_names_list)
})
names(cnb_score_cluster_stats_gam_AG_matched_by_cluster_1through10) <- cluster_names_list

#LM with mean-centered, squared age- quadratic term#

cnb_score_cluster_stats_lm_agesq_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
  cnb_score_cluster_stats_lm_agesq_AG_matched_withincluster<- lapply(cnb_measure_names_list, cluster=as.name(cluster_name), function(cnb_measure_name, cluster) 
  {
    cnb_measure <- as.name(cnb_measure_name)
    lm(substitute(cnb_measure ~ cluster + sex + age_in_years + ageSq , list(cnb_measure = cnb_measure, cluster = cluster)), data = subset_with_clusters_AG_matched)
  })
  setNames(cnb_score_cluster_stats_lm_agesq_AG_matched_withincluster, cnb_measure_names_list)
})
names(cnb_score_cluster_stats_lm_agesq_AG_matched_by_cluster_1through10) <- cluster_names_list


##### Just Hydra_3 clusters ######
#lm

cnb_score_cluster_stats_lm_AG_matched <- lapply(cnb_measure_names, function(x) 
{
  lm(substitute(i ~ Hydra_k3, list(i = as.name(x))), data = subset_with_clusters_AG_matched)
})
names(cnb_score_cluster_stats_lm_AG_matched) <- cnb_measure_names

#gam
cnb_score_cluster_stats_gam_AG_matched <- lapply(cnb_measure_names, function(x) 
{
  cnb_measure = as.name(x)
  gam(substitute(cnb_measure ~ Hydra_k3 + sex + s(age_in_years) , list(cnb_measure = cnb_measure)), data = subset_with_clusters_AG_matched, method="REML")
})
names(cnb_score_cluster_stats_gam_AG_matched) <- cnb_measure_names

#lm ageSq and mean centered
cnb_score_cluster_stats_lm_agesq_AG_matched <- lapply(cnb_measure_names, function(x) 
{
  lm(substitute(i ~ Hydra_k3 + sex + age_in_years + ageSq , list(i = as.name(x))), data = subset_with_clusters_AG_matched)
})
names(cnb_score_cluster_stats_lm_agesq_AG_matched) <- cnb_measure_names



##############################
####### Statistics ###########
##############################

######## All hydra clusters, Anova results ########

#lm
cnb_score_cluster_stats_anova_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
  cnb_score_cluster_stats_anova_AG_withincluster <- lapply(cnb_measure_names_list, cluster=as.name(cluster_name), function(cnb_measure_name, cluster) 
  {
     cnb_measure <- as.name(cnb_measure_name)
     anova(lm(substitute(cnb_measure ~ cluster, list(cnb_measure = cnb_measure, cluster = cluster)), data = subset_with_clusters_AG_matched))
  })
  setNames(cnb_score_cluster_stats_anova_AG_withincluster, cnb_measure_names_list)
})
names(cnb_score_cluster_stats_anova_AG_matched_by_cluster_1through10) <- cluster_names_list

#gam anova all clusters
cnb_score_cluster_stats_anova_gam_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
  cnb_score_cluster_stats_anova_gam_AG_withincluster <- lapply(cnb_measure_names_list, cluster=as.name(cluster_name), function(cnb_measure_name, cluster) 
  {
     cnb_measure <- as.name(cnb_measure_name)
     anova(gam(substitute(cnb_measure ~ cluster + sex + s(age_in_years) , list(cnb_measure = cnb_measure, cluster = cluster)), data = subset_with_clusters_AG_matched, method="REML"))
  })
  setNames(cnb_score_cluster_stats_anova_gam_AG_withincluster, cnb_measure_names_list)
})
names(cnb_score_cluster_stats_anova_gam_AG_matched_by_cluster_1through10) <- cluster_names_list

#lm agesq anova all clusters
cnb_score_cluster_stats_anova_lm_agesq_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
  cnb_score_cluster_stats_anova_lm_agesq_AG_withincluster <- lapply(cnb_measure_names_list, cluster=as.name(cluster_name), function(cnb_measure_name, cluster) 
  {
     cnb_measure <- as.name(cnb_measure_name)
     anova(lm(substitute(cnb_measure ~ cluster + sex + age_in_years + ageSq , list(cnb_measure = cnb_measure, cluster = cluster)), data = subset_with_clusters_AG_matched))
  })
  setNames(cnb_score_cluster_stats_anova_lm_agesq_AG_withincluster, cnb_measure_names_list)
})
names(cnb_score_cluster_stats_anova_lm_agesq_AG_matched_by_cluster_1through10) <- cluster_names_list


#####Just Hydra 3 clusters ANOVA ########
#lm Hydra K3 Anova
cnb_score_cluster_stats_anova_lm_AG_matched <- lapply(cnb_score_cluster_stats_lm_AG_matched, anova) 
names(cnb_score_cluster_stats_anova_lm_AG_matched) <- cnb_measure_names

#gam Hydra K3 ANOVA
cnb_score_cluster_stats_anova_gam_AG_matched <- lapply(cnb_score_cluster_stats_gam_AG_matched, anova)
names(cnb_score_cluster_stats_anova_gam_AG_matched) <- cnb_measure_names

#lm Hydra K3 Anova
cnb_score_cluster_stats_anova_lm_agesq_AG_matched <- lapply(cnb_score_cluster_stats_lm_agesq_AG_matched, anova) 
names(cnb_score_cluster_stats_anova_lm_agesq_AG_matched) <- cnb_measure_names





```

##Results graphically presented
```{r Results graphically presented, echo = FALSE}
###################################################
### Average Z-scores for accuracy and speed #######
###################################################
#Get stats of mean accuracy, processing speed and efficiency 
cluster_titles <- get_cluster_titles(hydra_cluster = num_clusters)
numeric_vector <- get_cluster_numerical_vector(hydra_cluster = num_clusters)
groups_list <- data.frame(cbind(c(cluster_titles), c(numeric_vector)))
names(groups_list) <- c("cl", "numeric")
all_mean_sd_sem <- data.frame(rep(groups_list$cl, length(summary_factor_scores)), rep(summary_factor_scores, each = length(numeric_vector)), rep(0, 1), rep(0, 1), rep(0,1))
names(all_mean_sd_sem) <- c("cl", "cnb", "mean", "sd", "sem")
for(cnb in summary_factor_scores){
  for(num in 1:length(numeric_vector)) {
    clst <- groups_list[num,1]
    meas <- groups_list[num,2]
    mean_for_eval <- paste("mean(subset_with_clusters_AG_matched$", cnb, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")])", sep="")
    mean_grp <- eval(parse(text=as.name(mean_for_eval)))
    all_mean_sd_sem$mean[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- mean_grp
    
    sd_for_eval <- paste("sd(subset_with_clusters_AG_matched$", cnb, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")])", sep="")
    sd_grp <- eval(parse(text=as.name(sd_for_eval)))
    all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- sd_grp
    #all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)]/sqrt(nrow(subset_with_clusters_AG_matched))
    sem_for_eval <- paste("sd(subset_with_clusters_AG_matched$", cnb, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")])/sqrt(length(which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")))", sep="")
    sem_grp <- eval(parse(text=as.name(sem_for_eval)))
    all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- sem_grp
  }
}
names(all_mean_sd_sem) <- c("cluster", "cnb", "mean", "sd", "sem")

#remove the NAR_Overall from everything
summary_scores_first_letter_cap <- c("Accuracy", "Speed", "Efficiency")
newNames<- rep(summary_scores_first_letter_cap, each = num_clusters + 1)
all_mean_sd_sem$newNames <- newNames

ggplot(data = all_mean_sd_sem, aes(x = factor(newNames, level = summary_scores_first_letter_cap), y = mean, group = cluster)) + ylab("Mean Z-score") + xlab("Summary Scores") + 
  ggtitle("CNB Summary Factor Scores") +
  geom_line(aes(color=cluster, size=.1), show.legend = F) +
  geom_point(aes(color=cluster)) + 
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.1, size=1.5) +
  scale_x_discrete(name = " ") +
  scale_y_continuous(limits=c(-1.5,1.5)) + 
  guides(colour = guide_legend(override.aes = list(size=10))) +
  theme(axis.text.x = element_text(size = 30), 
        axis.text.y = element_text(size = 30),
        title = element_text(size = 30), 
        legend.text = element_text(size = 30), 
        plot.title = element_text(size=35),
        legend.title=element_blank())
#####################################
###### By CNB Measure ###############
#####################################
#can do with all gender as well, as well as matched/unmatched, etc
#loop through each cluster and each cnb measure, make text and evaluate the following: mean of each cluster by measure, and sd of each cluster by measure
#SEM calculated by taking SD, and dividing by the square root of the number of people in the analysis... Should this be by # people in cluster?
cluster_titles <- get_cluster_titles(hydra_cluster = num_clusters)
numeric_vector <- get_cluster_numerical_vector(hydra_cluster = num_clusters)
groups_list <- data.frame(cbind(c(cluster_titles), c(numeric_vector)))
names(groups_list) <- c("cl", "numeric")
all_mean_sd_sem <- data.frame(rep(groups_list$cl, length(cnb_measure_names)), rep(cnb_measure_names, each = length(numeric_vector)), rep(0, 1), rep(0, 1), rep(0,1))
names(all_mean_sd_sem) <- c("cl", "cnb", "mean", "sd", "sem")
for(cnb in cnb_measure_names_list){
  for(num in 1:length(numeric_vector)) {
    clst <- groups_list[num,1]
    meas <- groups_list[num,2]
    mean_for_eval <- paste("mean(subset_with_clusters_AG_matched$", cnb, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")])", sep="")
    mean_grp <- eval(parse(text=as.name(mean_for_eval)))
    all_mean_sd_sem$mean[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- mean_grp
    
    sd_for_eval <- paste("sd(subset_with_clusters_AG_matched$", cnb, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")])", sep="")
    sd_grp <- eval(parse(text=as.name(sd_for_eval)))
    all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- sd_grp
    #all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)]/sqrt(nrow(subset_with_clusters_AG_matched))
    sem_for_eval <- paste("sd(subset_with_clusters_AG_matched$", cnb, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")])/sqrt(length(which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")))", sep="")
    sem_grp <- eval(parse(text=as.name(sem_for_eval)))
    all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- sem_grp
  }
}


#add sems to cnb_measures_for_plot
#cnb_measures_for_plot$sem <- all_sem_one_col
names(all_mean_sd_sem) <- c("cluster", "cnb", "mean", "sd", "sem")

ggplot(data = all_mean_sd_sem, aes(x = cnb, y = mean, group = cluster)) + ylab("Mean Z-score") + xlab("Summary Scores") + 
  ggtitle("CNB Measures") + 
  geom_line(aes(color=cluster, size=.1), show.legend = F) +
  geom_point(aes(color=cluster)) + 
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.1, size=1.5) +
  scale_x_discrete(name = " ") +
  scale_y_continuous(limits=c(-1.5,1.5)) + 
  guides(colour = guide_legend(override.aes = list(size=10))) +
  theme(axis.text.x = element_text(size = 30, angle=60, hjust = 1), 
        axis.text.y = element_text(size = 30),
        title = element_text(size = 30), 
        legend.text = element_text(size = 30), 
        plot.title = element_text(size=35),
        legend.title=element_blank())

####Accuracy alone####
cluster_titles <- get_cluster_titles(hydra_cluster = num_clusters)
numeric_vector <- get_cluster_numerical_vector(hydra_cluster = num_clusters)
groups_list <- data.frame(cbind(c(cluster_titles), c(numeric_vector)))
names(groups_list) <- c("cl", "numeric")
all_mean_sd_sem <- data.frame(rep(groups_list$cl, length(cnb_accuracy_names)), rep(cnb_accuracy_names, each = length(numeric_vector)), rep(0, 1), rep(0, 1), rep(0,1))
names(all_mean_sd_sem) <- c("cl", "cnb", "mean", "sd", "sem")
for(cnb in cnb_accuracy_names){
  for(num in 1:length(numeric_vector)) {
    clst <- groups_list[num,1]
    meas <- groups_list[num,2]
    mean_for_eval <- paste("mean(subset_with_clusters_AG_matched$", cnb, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")])", sep="")
    mean_grp <- eval(parse(text=as.name(mean_for_eval)))
    all_mean_sd_sem$mean[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- mean_grp
    
    sd_for_eval <- paste("sd(subset_with_clusters_AG_matched$", cnb, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")])", sep="")
    sd_grp <- eval(parse(text=as.name(sd_for_eval)))
    all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- sd_grp
    #all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)]/sqrt(nrow(subset_with_clusters_AG_matched))
    sem_for_eval <- paste("sd(subset_with_clusters_AG_matched$", cnb, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")])/sqrt(length(which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")))", sep="")
    sem_grp <- eval(parse(text=as.name(sem_for_eval)))
    all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- sem_grp
  }
}

#add sems to cnb_measures_for_plot
#cnb_measures_for_plot$sem <- all_sem_one_col
names(all_mean_sd_sem) <- c("cluster", "cnb", "mean", "sd", "sem")
accuracy_names_no_z <- gsub("_z", "", cnb_accuracy_names)
accuracy_full_names <- extended_names[1:12,2]

  ggplot(data = all_mean_sd_sem, aes(x = factor(cnb, level = cnb_accuracy_names), y = mean, group = cluster)) + ylab("Mean Z-score") + xlab("Accuracy") + 
  ggtitle("CNB Accuracy Measures") + 
  geom_line(aes(color=cluster, size=.1), show.legend = F) +
  geom_point(aes(color=cluster)) + 
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.1, size=1.5) +
 # scale_x_discrete(labels=accuracy_names_no_z) +
  scale_x_discrete(labels=accuracy_full_names, name = " ") +
  scale_y_continuous(limits=c(-1.5,1.5)) + 
  guides(colour = guide_legend(override.aes = list(size=10))) +
  theme(axis.text.x = element_text(size = 20, angle=60, hjust = 1), 
        axis.text.y = element_text(size = 30),
        title = element_text(size = 30), 
        legend.text = element_text(size = 30), 
        plot.title = element_text(size=35),
        legend.title=element_blank())

####Speed alone####
cluster_titles <- get_cluster_titles(hydra_cluster = num_clusters)
numeric_vector <- get_cluster_numerical_vector(hydra_cluster = num_clusters)
groups_list <- data.frame(cbind(c(cluster_titles), c(numeric_vector)))
names(groups_list) <- c("cl", "numeric")
all_mean_sd_sem <- data.frame(rep(groups_list$cl, length(cnb_speed_names)), rep(cnb_speed_names, each = length(numeric_vector)), rep(0, 1), rep(0, 1), rep(0,1))
names(all_mean_sd_sem) <- c("cl", "cnb", "mean", "sd", "sem")
for(cnb in cnb_speed_names){
  for(num in 1:length(numeric_vector)) {
    clst <- groups_list[num,1]
    meas <- groups_list[num,2]
    mean_for_eval <- paste("mean(subset_with_clusters_AG_matched$", cnb, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")])", sep="")
    mean_grp <- eval(parse(text=as.name(mean_for_eval)))
    all_mean_sd_sem$mean[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- mean_grp
    
    sd_for_eval <- paste("sd(subset_with_clusters_AG_matched$", cnb, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")])", sep="")
    sd_grp <- eval(parse(text=as.name(sd_for_eval)))
    all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- sd_grp
    #all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)]/sqrt(nrow(subset_with_clusters_AG_matched))
    sem_for_eval <- paste("sd(subset_with_clusters_AG_matched$", cnb, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")])/sqrt(length(which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups_list[num,2], ")))", sep="")
    sem_grp <- eval(parse(text=as.name(sem_for_eval)))
    all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$cnb == cnb)] <- sem_grp
  }
}


#add sems to cnb_measures_for_plot
#cnb_measures_for_plot$sem <- all_sem_one_col
names(all_mean_sd_sem) <- c("cluster", "cnb", "mean", "sd", "sem")
# string manipulation to get pretty labels
speed_names_no_s_z <- gsub("_s_z", "", cnb_speed_names)
speed_full_names <- extended_names[13:26,2]

ggplot(data = all_mean_sd_sem, aes(x = factor(cnb, level = cnb_speed_names), y = mean, group = cluster)) + ylab("Mean Z-score") + xlab("Summary Scores") + 
  ggtitle("CNB Speed Measures") + 
  geom_line(aes(color=cluster, size=.1), show.legend = F) +
  geom_point(aes(color=cluster)) + 
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.1, size=1.5) +
  scale_x_discrete(labels=speed_full_names, name = " ") +
  scale_y_continuous(limits=c(-1.5,1.5)) + 
  guides(colour = guide_legend(override.aes = list(size=10))) +
  theme(axis.text.x = element_text(size = 20, angle=60, hjust = 1), 
        axis.text.y = element_text(size = 30),
        title = element_text(size = 30), 
        legend.text = element_text(size = 30), 
        plot.title = element_text(size=35),
        legend.title=element_blank())

```



FDR correction 
```{r FDR Correction, echo = FALSE}

###################################################
## Extracting anovas with significant p values ####
###################################################
#lm
#Looking at Hydra_k3, but can redo with nested list
#Look at model summaries
models_anova <- lapply(cnb_score_cluster_stats_anova_lm_AG_matched, summary)

#Pull p-values
p_anova <- sapply(cnb_score_cluster_stats_anova_lm_AG_matched, function(v) v$"Pr(>F)"[1]) #$coef[,"Pr(>F)"][2]) #get the p value for dep binarized

#Convert to data frame
p_anova <- as.data.frame(p_anova)

#Print original p-values to three decimal places
p_round_anova <- round(p_anova,3)

#FDR correct p-values
pfdr_anova <- p.adjust(p_anova[,1],method="fdr")

#Convert to data frame
pfdr_anova <- as.data.frame(pfdr_anova)
row.names(pfdr_anova) <- cnb_measure_names

#To print fdr-corrected p-values to three decimal places
pfdr_round_anova <- round(pfdr_anova,3)

#List the NMF components that survive FDR correction
cnb_fdr_anova <- row.names(pfdr_anova)[pfdr_anova<0.05]

#make a data frame with names and fdr values (rounded to 3 decimals)
cnb_names_and_fdr_values_anova <- data.frame(cbind(cnb_fdr_anova, round(pfdr_anova[pfdr_anova<0.05],3)))

#add titles to names_and_fdr tables
names(cnb_names_and_fdr_values_anova) <- c("cnb_measure", "p_FDR_corr")

print("LM")
print(cnb_names_and_fdr_values_anova)

#gam

#Looking at Hydra_k3, but can redo with nested list
#Look at model summaries
#models_anova <- lapply(cnb_score_cluster_stats_anova_gam_AG_matched, summary)

#Pull p-values
p_anova <- sapply(cnb_score_cluster_stats_anova_gam_AG_matched, function(v) v$pTerms.table[1,3])
                    #"Pr(>F)"[1]) #$coef[,"Pr(>F)"][2]) #get the p value for dep binarized

#Convert to data frame
p_anova <- as.data.frame(p_anova)

#Print original p-values to three decimal places
p_round_anova <- round(p_anova,3)

#FDR correct p-values
pfdr_anova <- p.adjust(p_anova[,1],method="fdr")

#Convert to data frame
pfdr_anova <- as.data.frame(pfdr_anova)
row.names(pfdr_anova) <- cnb_measure_names

#To print fdr-corrected p-values to three decimal places
pfdr_round_anova <- round(pfdr_anova,3)

#List the NMF components that survive FDR correction
cnb_fdr_anova <- row.names(pfdr_anova)[pfdr_anova<0.05]

#make a data frame with names and fdr values (rounded to 3 decimals)
cnb_names_and_fdr_values_anova <- data.frame(cbind(cnb_fdr_anova, round(pfdr_anova[pfdr_anova<0.05],3)))

#add titles to names_and_fdr tables
names(cnb_names_and_fdr_values_anova) <- c("cnb_measure", "p_FDR_corr_GAM")

print("GAM")
print(cnb_names_and_fdr_values_anova)

#lm agesq
#Looking at Hydra_k3
#Look at model summaries
models_anova_lm_agesq <- lapply(cnb_score_cluster_stats_anova_lm_agesq_AG_matched, summary)

#Pull p-values
p_anova_lm_agesq <- sapply(cnb_score_cluster_stats_anova_lm_agesq_AG_matched, function(v) v$"Pr(>F)"[1]) #$coef[,"Pr(>F)"][2]) #get the p value for dep binarized

#Convert to data frame
p_anova_lm_agesq <- as.data.frame(p_anova_lm_agesq)

#Print original p-values to three decimal places
p_round_anova_lm_agesq <- round(p_anova_lm_agesq,3)

#FDR correct p-values
pfdr_anova_lm_agesq <- p.adjust(p_anova_lm_agesq[,1],method="fdr")

#Convert to data frame
pfdr_anova_lm_agesq <- as.data.frame(pfdr_anova_lm_agesq)
row.names(pfdr_anova_lm_agesq) <- cnb_measure_names

#To print fdr-corrected p-values to three decimal places
pfdr_round_anova_lm_agesq <- round(pfdr_anova_lm_agesq,3)

#List the NMF components that survive FDR correction
cnb_fdr_anova_lm_agesq <- row.names(pfdr_anova_lm_agesq)[pfdr_anova_lm_agesq<0.05]

#make a data frame with names and fdr values (rounded to 3 decimals)
cnb_names_and_fdr_values_anova_lm_agesq <- data.frame(cbind(cnb_fdr_anova_lm_agesq, round(pfdr_anova_lm_agesq[pfdr_anova_lm_agesq<0.05],3)))

#add titles to names_and_fdr tables
names(cnb_names_and_fdr_values_anova_lm_agesq) <- c("cnb_measure", "p_FDR_corr")

print("LM Agesq- Mean centered age that was then squared")
print(cnb_names_and_fdr_values_anova_lm_agesq)

######################################################
####Pairwise t-tests for anova-corrected lm means ####
######################################################

#put lm model into emmeans format
cnb_emmodel_lm_agesq_AG_matched <- lapply(cnb_score_cluster_stats_lm_agesq_AG_matched, function(x) {as.list(ref_grid(x))})
cnb_emmgrid_lm_agesq_AG_matched <- lapply(cnb_emmodel_lm_agesq_AG_matched, function(x) {as.emmGrid(x)})

#run emmeans, do not include values that were not FDR corrected
cnb_emmeans_lm_agesq_AG_matched <- lapply(cnb_emmgrid_lm_agesq_AG_matched, function(x) {emmeans(x, "Hydra_k3")})

#run pairwise contrasts
cnb_emmpairs_lm_agesq_AG_matched <- lapply(cnb_emmeans_lm_agesq_AG_matched, function(x) {pairs(x)})

#Only include stuff that was fdr corrected (i.e., only keep parts of the model (or only display) ones that are corrected)
cnb_emmpairs_lm_agesq_AG_matched_FDR_corrected <- cnb_emmpairs_lm_agesq_AG_matched[c(cnb_fdr_anova_lm_agesq)]

######Make table of contrasts, rows are names of cnb measures that are fdr corrected, columns are contrasts, values are pvalues

#contrast names, -1 = controls, 1-3 are clusters
#contrast_names <- c("-1 - 1", "-1 - 2", "-1 - 3", "1 - 2", "1 - 3", "2 - 3")
contrast_names <- make_pairwise_contrast_names(num_clusters = num_clusters)
#go through each fdr corrected cnb measure, and extract p values
contrast_table <- lapply(cnb_emmpairs_lm_agesq_AG_matched_FDR_corrected, function(x) {round(summary(x)$p.value,3)})
#get the names of the measures that were fdr corrected
fdr_corrected_cnb <- names(contrast_table)
#build table that will hold the name of the measure and the p values
pairwise_table <- data.frame(matrix(nrow = length(fdr_corrected_cnb), ncol = length(contrast_names)))
#give the appropriate names
rownames(pairwise_table) <- fdr_corrected_cnb
colnames(pairwise_table) <- contrast_names

#loop through each measure, and manually assign the columns to be the p values
for (measure in fdr_corrected_cnb)
{
  pair_pval <- contrast_table[[measure]]
  pairwise_table[measure,] <- pair_pval
}

#add FDR correction
pairwise_table_with_fdr <- pairwise_table
pairwise_table_with_fdr$p_FDR_corr <- cnb_names_and_fdr_values_anova_lm_agesq$p_FDR_corr


#print values
print("LM Agesq pairwise contrasts for FDR corrected values, CNB scores")
print(pairwise_table)

print("LM Agesq pairwise contrasts with FDR corrected values, CNB scores")
print(pairwise_table_with_fdr)

sapply(cnb_emmpairs_lm_agesq_AG_matched_FDR_corrected, function(x) {print(x)})

#########################################################
#checkmodel with visreg, uncomment when want to check####
#########################################################
invisible(lapply(cnb_score_cluster_stats_lm_AG_matched, function(x) {visreg(x)}))

```


