---
title: "Cortical_volume_analysis_matched_age_and_sex_imaging_k3"
author: "Erica Baller"
date: "6/29/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 9)
library(visreg)
library(mgcv)
library(tableone)
library(dplyr)
library(plm)
library(MatchIt)
library(tidyr)
library(ggplot2)
library(reshape)
library(emmeans)
theme_update(plot.title = element_text(hjust = 0.5))
source("~/BBL/from_chead/ballerDepHeterogen/ballerDepHeterogenScripts/Hydra_functions.R")

```

## R Markdown

This script goes through demographics, volume scores, health, and psych summaries, adds clustering information, runs statistics and makes graphs from results.

Part 1 : Read in csv.s
  -This script reads in demographics, volume_scores, health and psych summaries, merges them, removes NAs, codes and separates by depression.

Part 2 : merge with hydra
  -It then merges these documents with hydra output (made in cbica), adding Hydra_k1 through Hydra_k10 columns (which represent the number of clusters)
  -The script reads in 3 different types of groups (matched)

Part 3 : Demographics tables
  - Demographics tables matched
  
Part 4 : Graphing
  - Graphs were then made.  
    *For continuous variables(age, medu1), the graphs represent means, with SEM as error bars
    *For categorical variables (race, sex) the graphs are percentages (caucasian, male) per group, with chisq used to calculate significance

Part 5 : LM/GAM/LM with Agesq
  -The script then runs LM on each cognitive score (volume_measure ~ hydra_group). 
   - Does gam (volume_measure ~ hydra_group + s(age) + sex + averageManualRating)
   - Does LM with ageSq (volume_measure ~ hydra_group + ageSq + sex + averageManualRating)
  -There is a test option that does this for all volume measures and all hydra groups, but for the remainder of the analysis, Hydra_k3 was the only classification more deeply explored.

Part 6 : Anovas
  -Anovas were also run on the results of the LM of each volume value by cluster.


Part 7 : FDR Correction
  -FDR correction was calculated for each volume measure ANOVA output
  -A table of the results was extracted
  


```{r volume, echo = FALSE}
#######################################################
############ READ IN, MERGE AND SUBSET DATA############
#######################################################
num_clusters <- 3
cluster_titles <- get_cluster_titles(hydra_cluster = num_clusters)

#read in csvs
demographics <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/n9498_demographics_go1_20161212.csv", header = TRUE, sep = ",") #from /data/joy/BBL/projevolumes/ballerDepHeterogen/data/n9498_demographics_go1_20161212.csv
cnb_scores <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/n9498_cnb_zscores_fr_20170202.csv", header = TRUE, sep = ",") #from /data/joy/BBL/projects/ballerDepHeterogen/data/n9498_cnb_zscores_fr_20170202.csv
health <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/n9498_health_20170405.csv", header = TRUE, sep = ",") #from /data/joy/BBL/projects/ballerDepHeterogen/data/n9498_health_20170405.csv
psych_summary <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/n9498_goassess_psych_summary_vars_20131014.csv", header = TRUE, sep = ",") #from /data/joy/BBL/projects/ballerDepHeterogen/data/n9498_goassess_psych_summary_vars_20131014.csv
t1_qa_scores <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/neuroimaging/t1struct/n1601_t1QaData_20170306.csv", header = TRUE, sep = ",") 
jlfvolume_summary <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/neuroimaging/t1struct/n1601_jlfAntsCTIntersectionVol_20170412.csv", header = TRUE, sep = ",") 



#read in Hydra cluster data -> AG (all_gender), M(males), F(females) 
hydra_AG_matched_clusters <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/hydra_output_from_cbica/hydra_matched/matched_imaging_plus_non_imaging/CogData_matched_age_and_sex_n1424_matched_imaging_plus_non_imaging_HydraSubtypes.csv", header = TRUE, sep = ",")

#Coerce hydra values into factor format
hydra_names <- names(hydra_AG_matched_clusters[2:11])
hydra_AG_matched_clusters[hydra_names] <- lapply(hydra_AG_matched_clusters[hydra_names], factor)


############
#prepping and merging 
############

#remove people with NA for race, age, or sex.  START WITH N = 9498
demographics_noNA_race <- demographics[!is.na(demographics$race),] #everyone has a race, N = 9498
demographics_noNA_race_age <- demographics_noNA_race[!is.na(demographics_noNA_race$ageAtClinicalAssess1),] # 86 people do not have age at clinical assessment.  N = 9412
demographics_noNA_race_age_sex <- demographics_noNA_race_age[!is.na(demographics_noNA_race_age$sex),] #everyone has a sex, N = 9412
demographics_noNA_race_age_andCNBage_sex <- demographics_noNA_race_age_sex[!is.na(demographics_noNA_race_age_sex$ageAtCnb1),] #6 people do not have ageAtCnb1, N = 9406

#remove people with NA for depression or total psych score, START WITH N = 9498
psych_summary_no_NA_dep <- psych_summary[!is.na(psych_summary$smry_dep),] #take out those with NA for depression, 87 people N = 9411
psych_summary_no_NA_dep_and_smry_psych_overall <- psych_summary_no_NA_dep[!is.na(psych_summary_no_NA_dep$smry_psych_overall_rtg),] #take out those with NA for overall psych rtg, no additional people lost, N = 9411

#remove people with excluded imaging

t1_struct_include = subset.data.frame(t1_qa_scores, (t1Exclude == 0))

#merge demographics and imaging #this is if we want to include people without full demographic data
dem_cnb <- merge(demographics_noNA_race_age_andCNBage_sex, cnb_scores, by = "bblid") #merge demographics and cnb, N = 9406
psych_health <- merge(psych_summary_no_NA_dep_and_smry_psych_overall, health, by = "bblid") #merge psych and health, N = 9411
dem_cnb_psych_health <- merge(dem_cnb, psych_health, by = "bblid") #merge all 4 csvs, lost 1 person [134716] (had demographics, but no psych ratings): N = 9405
t1_qa_and_jlfvolume = merge(t1_struct_include, jlfvolume_summary, by = "bblid")

dem_psych_health_qa_volume_merged <- merge (dem_cnb_psych_health, t1_qa_and_jlfvolume, by = "bblid") 
#dem_cnb_psych_health_factor_scores_merged <- merge(dem_cnb_psych_health_merged, cnb_factor_scores, by = "bblid")

#make subsets
subset_just_dep_and_no_medicalratingExclude <- subset.data.frame(dem_psych_health_qa_volume_merged, (medicalratingExclude == 0) & (smry_dep == 4), select = "bblid") 
subset_no_psych_no_medicalratingExclude <- subset.data.frame(dem_psych_health_qa_volume_merged, (medicalratingExclude == 0) & (smry_psych_overall_rtg < 4), select = "bblid") 
subset_dep_or_no_psych_and_no_medicalratingExclude <- subset.data.frame(dem_psych_health_qa_volume_merged, (medicalratingExclude == 0) & ((smry_dep == 4) | (smry_psych_overall_rtg <4))) 

#would binarize depression smry score to -1 (less than 4, not depressed) and 1 (score 4 , depressed)
dep_binarized <- ifelse(subset_dep_or_no_psych_and_no_medicalratingExclude$smry_dep == 4, 1, -1)
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED <- cbind(subset_dep_or_no_psych_and_no_medicalratingExclude, dep_binarized) #N = 3284

#make depression and gender into factor scores
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$dep_binarized <- as.factor(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$dep_binarized)
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$sex <- as.factor(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$sex)

#divide ageAtCNB by 12 for age
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$age_in_years <- subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$ageAtCnb1/12

#race binarized for plotting purposes, caucasian 1, non-caucasion 0
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$race_binarized <- ifelse(as.factor(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$race) == 1, 1, 0)

#add age squared mean-centered term for use in LM
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$ageSq <- as.numeric(I(scale(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$age_in_years, scale = FALSE, center = TRUE)^2))

#remove people with NA in their cognitive measures
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED <- subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED[complete.cases(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED[14:39]),]

################################################
### Merge clustering data with subsetted data ##
################################################

#AG (all gender), M (males), F (females) 
#AG Matched - n 1424

subset_with_clusters_AG_matched <- merge(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED, hydra_AG_matched_clusters, by = "bblid")



```

##Demographics

```{r Demographics, echo = FALSE}
#############################
####### Demographics ########
#############################
subset_with_clusters_AG_matched <- merge(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED, hydra_AG_matched_clusters, by = "bblid")



```


```{r Graphs by cluster, echo=FALSE}

#######Chi-square for males/females and race########
##########By males, and by caucasians ##############


#Chi squared 
chisq_matched_sex <- chi_sq(data_frame = subset_with_clusters_AG_matched, "sex", num_clusters)
chisq_matched_race <- chi_sq(data_frame = subset_with_clusters_AG_matched, "race_binarized", num_clusters)

#get means/stds
total_people_Hydra <- total_people_per_cluster(data_frame = subset_with_clusters_AG_matched, hydra_cluster = num_clusters)

num_men_all_clusters <- total_people_per_cluster_by_group(data_frame = subset_with_clusters_AG_matched, variable = "sex", hydra_cluster = num_clusters, group_val = 1)
num_caucasian_all_clusters <- total_people_per_cluster_by_group(data_frame = subset_with_clusters_AG_matched, variable = "race_binarized", hydra_cluster = num_clusters, group_val = 1)

percent_men_all_clusters <- (num_men_all_clusters/total_people_Hydra) * 100
percent_caucasian_all_clusters <- (num_caucasian_all_clusters/total_people_Hydra)*100

p_values <- c("", chisq_matched_sex$p.value, "", chisq_matched_race$p.value)

dat_sex_race <- data.frame(cl = c(cluster_titles, "Significance"), 
                           num_males = c(num_men_all_clusters, "---"),
                           percent_males = round(c(percent_men_all_clusters, chisq_matched_sex$p.value), 2), 
                           num_caucasians = c(num_caucasian_all_clusters, "---"),
                           percent_caucasian = round(c(percent_caucasian_all_clusters, chisq_matched_race$p.value),2))
dat_sex_race_no_significance <-  data.frame(cl = cluster_titles, 
                                            num_males = (num_men_all_clusters),
                                            percent_males = percent_men_all_clusters, 
                                            num_caucasians = num_caucasian_all_clusters,
                                            percent_caucasian = percent_caucasian_all_clusters)                 
percentages <- data.frame(cl=cluster_titles, percent_males = percent_men_all_clusters, percent_caucasians = percent_caucasian_all_clusters)
percentages_for_plot <- melt(percentages, id.vars = "cl")
names(percentages_for_plot) <- c("cluster", "group", "percent")

#Set Titles for plots
title1 <- paste0("Hydra_k", num_clusters, " Percentages")

if(chisq_matched_sex$p.value < 0.05) {
  title2 <- paste0("Hydra_k", num_clusters, "% Male, p < 0.05")
} else {
  title2 <- paste0("Hydra_k", num_clusters, "% Male, p = ", round(chisq_matched_sex$p.value, 2))
}

if(chisq_matched_race$p.value < 0.05) {
  title3 <- paste0("Hydra_k", num_clusters, "% Caucasian, p < 0.05")
} else {
  title3 <- paste0("Hydra_k", num_clusters, "% Caucasian, p = ", round(chisq_matched_race$p.value, 2))
}

#plot
ggplot(data = percentages_for_plot, aes(x = group, y = percent, group = cluster)) + 
  geom_line(aes(color=cluster)) +
  geom_point(aes(color=cluster)) + 
  ggtitle(title1)

ggplot(dat_sex_race_no_significance, aes(x = cl, y = percent_males, fill=cl)) + geom_col() +
  scale_x_discrete(limits=cluster_titles) + ylim(0, 100) + xlab("Clusters") + ylab("% Male") + 
  ggtitle(title2) + scale_fill_discrete(breaks=cluster_titles) +
  guides(fill=guide_legend(title=NULL))

ggplot(dat_sex_race_no_significance, aes(x = cl, y = percent_caucasian, fill=cl)) + geom_col() + 
  scale_x_discrete(limits=cluster_titles) + ylim(0, 100) + xlab("Clusters") + ylab("% Caucasian") + 
  ggtitle(title3) + scale_fill_discrete(breaks=cluster_titles) + 
  guides(fill=guide_legend(title=NULL))

#############################
######### Bar Graphs ########
#############################

variable_name_string <- c("age", "medu") #this allows you to specify the actual titles, if different from the data frame titles
plot_list <- plot_continuous_variables(data_frame = subset_with_clusters_AG_matched, var1 = "age_in_years", var2 = "medu1", hydra_cluster = num_clusters, optional_variable_name_string = variable_name_string)
for(x in 1:length(plot_list)){
  print(plot_list[[x]])
}



```

```{r stats, echo = FALSE}
#################################
# Linear Model for each measure #
##### Results stored in list ####
#################################

#get volume measure names
volume_measure_names <- names(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED)[grep("_vol_", names(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED))] #get the names of all the columns with _vol in the name
cluster_names <- colnames(hydra_AG_matched_clusters[,2:11])

volume_measure_names_list <- names(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED)[grep("_vol_", names(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED))] #get the names of all the columns with _vol_ in the name
cluster_names_list <- colnames(hydra_AG_matched_clusters[,2:11])

#### All Hydra clusters in embedded lis t######
volume_score_cluster_stats_lm_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
  volume_score_cluster_stats_lm_AG_matched_withincluster<- lapply(volume_measure_names_list, cluster=as.name(cluster_name), function(volume_measure_name, cluster) 
  {
    volume_measure <- as.name(volume_measure_name)
    lm(substitute(volume_measure ~ cluster + averageManualRating, list(volume_measure = volume_measure, cluster = cluster)), data = subset_with_clusters_AG_matched)
  })
  setNames(volume_score_cluster_stats_lm_AG_matched_withincluster, volume_measure_names_list)
})

names(volume_score_cluster_stats_lm_AG_matched_by_cluster_1through10) <- cluster_names_list


#gam
volume_score_cluster_stats_gam_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
 volume_score_cluster_stats_gam_AG_matched_withincluster<- lapply(volume_measure_names_list, cluster=as.name(cluster_name),   function(volume_measure_name, cluster) 
 {
    volume_measure <- as.name(volume_measure_name)
    gam(substitute(volume_measure ~ cluster + sex + s(age_in_years) + averageManualRating, list(volume_measure = volume_measure, cluster = cluster)), data = subset_with_clusters_AG_matched)
  })
 setNames(volume_score_cluster_stats_gam_AG_matched_withincluster, volume_measure_names_list)
})
names(volume_score_cluster_stats_gam_AG_matched_by_cluster_1through10) <- cluster_names_list

#LM with mean-centered, squared age- quadratic term#

volume_score_cluster_stats_lm_agesq_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
  volume_score_cluster_stats_lm_agesq_AG_matched_withincluster<- lapply(volume_measure_names_list, cluster=as.name(cluster_name), function(volume_measure_name, cluster) 
  {
    volume_measure <- as.name(volume_measure_name)
    lm(substitute(volume_measure ~ cluster + sex + age_in_years + ageSq + averageManualRating, list(volume_measure = volume_measure, cluster = cluster)), data = subset_with_clusters_AG_matched)
  })
  setNames(volume_score_cluster_stats_lm_agesq_AG_matched_withincluster, volume_measure_names_list)
})
names(volume_score_cluster_stats_lm_agesq_AG_matched_by_cluster_1through10) <- cluster_names_list


##### Just Hydra_3 clusters ######
#lm
volume_score_cluster_stats_lm_AG_matched <- lapply(volume_measure_names, function(x) 
{
  lm(substitute(i ~ Hydra_k3 + averageManualRating, list(i = as.name(x))), data = subset_with_clusters_AG_matched)
})
names(volume_score_cluster_stats_lm_AG_matched) <- volume_measure_names

#gam
volume_score_cluster_stats_gam_AG_matched <- lapply(volume_measure_names, function(x) 
{
  volume_measure = as.name(x)
  gam(substitute(volume_measure ~ Hydra_k3 + sex + s(age_in_years) + averageManualRating, list(volume_measure = volume_measure)), data = subset_with_clusters_AG_matched)
})
names(volume_score_cluster_stats_gam_AG_matched) <- volume_measure_names

#lm ageSq and mean centered
volume_score_cluster_stats_lm_agesq_AG_matched <- lapply(volume_measure_names, function(x) 
{
  lm(substitute(i ~ Hydra_k3 + sex + age_in_years + ageSq + averageManualRating, list(i = as.name(x))), data = subset_with_clusters_AG_matched)
})
names(volume_score_cluster_stats_lm_agesq_AG_matched) <- volume_measure_names



##############################
####### Statistics ###########
##############################

######## All hydra clusters, Anova results ########

#lm
volume_score_cluster_stats_anova_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
  volume_score_cluster_stats_anova_AG_withincluster <- lapply(volume_measure_names_list, cluster=as.name(cluster_name), function(volume_measure_name, cluster) 
  {
     volume_measure <- as.name(volume_measure_name)
     anova(lm(substitute(volume_measure ~ cluster + averageManualRating, list(volume_measure = volume_measure, cluster = cluster)), data = subset_with_clusters_AG_matched))
  })
  setNames(volume_score_cluster_stats_anova_AG_withincluster, volume_measure_names_list)
})
names(volume_score_cluster_stats_anova_AG_matched_by_cluster_1through10) <- cluster_names_list

#gam anova all clusters
volume_score_cluster_stats_anova_gam_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
  volume_score_cluster_stats_anova_gam_AG_withincluster <- lapply(volume_measure_names_list, cluster=as.name(cluster_name), function(volume_measure_name, cluster) 
  {
     volume_measure <- as.name(volume_measure_name)
     anova(gam(substitute(volume_measure ~ cluster + sex + s(age_in_years) + averageManualRating, list(volume_measure = volume_measure, cluster = cluster)), data = subset_with_clusters_AG_matched))
  })
  setNames(volume_score_cluster_stats_anova_gam_AG_withincluster, volume_measure_names_list)
})
names(volume_score_cluster_stats_anova_gam_AG_matched_by_cluster_1through10) <- cluster_names_list

#lm agesq anova all clusters
volume_score_cluster_stats_anova_lm_agesq_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
  volume_score_cluster_stats_anova_lm_agesq_AG_withincluster <- lapply(volume_measure_names_list, cluster=as.name(cluster_name), function(volume_measure_name, cluster) 
  {
     volume_measure <- as.name(volume_measure_name)
     anova(lm(substitute(volume_measure ~ cluster + sex + age_in_years + ageSq + averageManualRating, list(volume_measure = volume_measure, cluster = cluster)), data = subset_with_clusters_AG_matched))
  })
  setNames(volume_score_cluster_stats_anova_lm_agesq_AG_withincluster, volume_measure_names_list)
})
names(volume_score_cluster_stats_anova_lm_agesq_AG_matched_by_cluster_1through10) <- cluster_names_list


#####Just Hydra 3 clusters ANOVA ########
#lm Hydra K3 Anova
volume_score_cluster_stats_anova_lm_AG_matched <- lapply(volume_score_cluster_stats_lm_AG_matched, anova) 
names(volume_score_cluster_stats_anova_lm_AG_matched) <- volume_measure_names

#gam Hydra K3 ANOVA
volume_score_cluster_stats_anova_gam_AG_matched <- lapply(volume_score_cluster_stats_gam_AG_matched, anova)
names(volume_score_cluster_stats_anova_gam_AG_matched) <- volume_measure_names

#lm Hydra K3 Anova
volume_score_cluster_stats_anova_lm_agesq_AG_matched <- lapply(volume_score_cluster_stats_lm_agesq_AG_matched, anova) 
names(volume_score_cluster_stats_anova_lm_agesq_AG_matched) <- volume_measure_names

```

##Results graphically presented
```{r Results graphically presented, echo = FALSE}


#####################################
###### By volume Measure ###############
#####################################
#can do with all gender as well, as well as matched/unmatched, etc
#loop through each cluster and each volume measure, make text and evaluate the following: mean of each cluster by measure, and sd of each cluster by measure
#SEM calculated by taking SD, and dividing by the square root of the number of people in the analysis... Should this be by # people in cluster?


groups_list <- data.frame(cbind(c("TD", "Cluster1", "Cluster2", "Cluster3"), c("-1", "1", "2", "3")))
names(groups_list) <- c("cl", "numeric")
all_mean_sd_sem <- data.frame(rep(groups_list$cl, 129), rep(volume_measure_names, each = 4), rep(0, 1), rep(0, 1), rep(0,1))
names(all_mean_sd_sem) <- c("cl", "volume", "mean", "sd", "sem")
for(volume in volume_measure_names_list){
  for(num in 1:4) {
    clst <- groups_list[num,1]
    meas <- groups_list[num,2]
    mean_for_eval <- paste("mean(subset_with_clusters_AG_matched$", volume, "[which(subset_with_clusters_AG_matched$Hydra_k3 == ", groups_list[num,2], ")])", sep="")
    mean_grp <- eval(parse(text=as.name(mean_for_eval)))
    all_mean_sd_sem$mean[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$volume == volume)] <- mean_grp
    
    sd_for_eval <- paste("sd(subset_with_clusters_AG_matched$", volume, "[which(subset_with_clusters_AG_matched$Hydra_k3 == ", groups_list[num,2], ")])", sep="")
    sd_grp <- eval(parse(text=as.name(sd_for_eval)))
    all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$volume == volume)] <- sd_grp
  #  all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$volume == volume)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$volume == volume)]/sqrt(nrow(subset_with_clusters_AG_matched))
    sem_for_eval <- paste("sd(subset_with_clusters_AG_matched$", volume, "[which(subset_with_clusters_AG_matched$Hydra_k3 == ", groups_list[num,2], ")])/sqrt(length(which(subset_with_clusters_AG_matched$Hydra_k3 == ", groups_list[num,2], ")))", sep="")
    sem_grp <- eval(parse(text=as.name(sem_for_eval)))
    all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$volume == volume)] <- sem_grp
  }
}


#add sems to volume_measures_for_plot
#volume_measures_for_plot$sem <- all_sem_one_col
#names(volume_measures_for_plot) <- c("cluster", "volume", "z_score", "sem")
ggplot(data = all_mean_sd_sem, aes(x = volume, y = mean, group = cl)) +  ylab("Mean Volume") +
  geom_line(aes(color=cl)) +
  geom_point(aes(color=cl)) + 
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.1) +
  ggtitle("Hydra_k3 by volume Measures")

```

FDR correction 
```{r FDR Correction, echo = FALSE, fig.width=10}

###################################################
## Extracting anovas with significant p values ####
###################################################
#lm
#Looking at Hydra_k3, but can redo with nested list
#Look at model summaries
models_anova <- lapply(volume_score_cluster_stats_anova_lm_AG_matched, summary)

#Pull p-values
p_anova <- sapply(volume_score_cluster_stats_anova_lm_AG_matched, function(v) v$"Pr(>F)"[1]) #$coef[,"Pr(>F)"][2]) #get the p value for dep binarized

#Convert to data frame
p_anova <- as.data.frame(p_anova)

#Print original p-values to three decimal places
p_round_anova <- round(p_anova,3)

#FDR correct p-values
pfdr_anova <- p.adjust(p_anova[,1],method="fdr")

#Convert to data frame
pfdr_anova <- as.data.frame(pfdr_anova)
row.names(pfdr_anova) <- volume_measure_names

#To print fdr-corrected p-values to three decimal places
pfdr_round_anova <- round(pfdr_anova,3)

#List the NMF components that survive FDR correction
volume_fdr_anova <- row.names(pfdr_anova)[pfdr_anova<0.05]

#make a data frame with names and fdr values (rounded to 3 decimals)
volume_names_and_fdr_values_anova <- data.frame(cbind(volume_fdr_anova, round(pfdr_anova[pfdr_anova<0.05],3)))

#add titles to names_and_fdr tables
names(volume_names_and_fdr_values_anova) <- c("volume_measure", "p_FDR_corr")

print("LM")
print(volume_names_and_fdr_values_anova)

#gam

#Looking at Hydra_k3, but can redo with nested list
#Look at model summaries
#models_anova <- lapply(volume_score_cluster_stats_anova_gam_AG_matched, summary)

#Pull p-values
p_anova <- sapply(volume_score_cluster_stats_anova_gam_AG_matched, function(v) v$pTerms.table[1,3])
                    #"Pr(>F)"[1]) #$coef[,"Pr(>F)"][2]) #get the p value for dep binarized

#Convert to data frame
p_anova <- as.data.frame(p_anova)

#Print original p-values to three decimal places
p_round_anova <- round(p_anova,3)

#FDR correct p-values
pfdr_anova <- p.adjust(p_anova[,1],method="fdr")

#Convert to data frame
pfdr_anova <- as.data.frame(pfdr_anova)
row.names(pfdr_anova) <- volume_measure_names

#To print fdr-corrected p-values to three decimal places
pfdr_round_anova <- round(pfdr_anova,3)

#List the NMF components that survive FDR correction
volume_fdr_anova <- row.names(pfdr_anova)[pfdr_anova<0.05]

#make a data frame with names and fdr values (rounded to 3 decimals)
volume_names_and_fdr_values_anova <- data.frame(cbind(volume_fdr_anova, round(pfdr_anova[pfdr_anova<0.05],3)))

#add titles to names_and_fdr tables
names(volume_names_and_fdr_values_anova) <- c("volume_measure", "p_FDR_corr_GAM")

print("GAM")
print(volume_names_and_fdr_values_anova)

#lm agesq
#Looking at Hydra_k3
#Look at model summaries
models_anova_lm_agesq <- lapply(volume_score_cluster_stats_anova_lm_agesq_AG_matched, summary)

#Pull p-values
p_anova_lm_agesq <- sapply(volume_score_cluster_stats_anova_lm_agesq_AG_matched, function(v) v$"Pr(>F)"[1]) #$coef[,"Pr(>F)"][2]) #get the p value for dep binarized

#Convert to data frame
p_anova_lm_agesq <- as.data.frame(p_anova_lm_agesq)

#Print original p-values to three decimal places
p_round_anova_lm_agesq <- round(p_anova_lm_agesq,3)

#FDR correct p-values
pfdr_anova_lm_agesq <- p.adjust(p_anova_lm_agesq[,1],method="fdr")

#Convert to data frame
pfdr_anova_lm_agesq <- as.data.frame(pfdr_anova_lm_agesq)
row.names(pfdr_anova_lm_agesq) <- volume_measure_names

#To print fdr-corrected p-values to three decimal places
pfdr_round_anova_lm_agesq <- round(pfdr_anova_lm_agesq,3)

#List the NMF components that survive FDR correction
volume_fdr_anova_lm_agesq <- row.names(pfdr_anova_lm_agesq)[pfdr_anova_lm_agesq<0.05]

#make a data frame with names and fdr values (rounded to 3 decimals)
volume_names_and_fdr_values_anova_lm_agesq <- data.frame(cbind(volume_fdr_anova_lm_agesq, round(pfdr_anova_lm_agesq[pfdr_anova_lm_agesq<0.05],3)))

#add titles to names_and_fdr tables
names(volume_names_and_fdr_values_anova_lm_agesq) <- c("volume_measure", "p_FDR_corr")

print("LM Agesq- Mean centered age that was then squared")
print(volume_names_and_fdr_values_anova_lm_agesq)

######################################################
####Pairwise t-tests for anova-corrected lm means ####
######################################################

#put lm model into emmeans format
volume_emmodel_lm_agesq_AG_matched <- lapply(volume_score_cluster_stats_lm_agesq_AG_matched, function(x) {as.list(ref_grid(x))})
volume_emmgrid_lm_agesq_AG_matched <- lapply(volume_emmodel_lm_agesq_AG_matched, function(x) {as.emmGrid(x)})

#run emmeans, do not include values that were not FDR corrected
volume_emmeans_lm_agesq_AG_matched <- lapply(volume_emmgrid_lm_agesq_AG_matched, function(x) {emmeans(x, "Hydra_k3")})

#run pairwise contrasts
volume_emmpairs_lm_agesq_AG_matched <- lapply(volume_emmeans_lm_agesq_AG_matched, function(x) {pairs(x)})

#Only include stuff that was fdr corrected (i.e., only keep parts of the model (or only display) ones that are corrected)
volume_emmpairs_lm_agesq_AG_matched_FDR_corrected <- volume_emmpairs_lm_agesq_AG_matched[c(volume_fdr_anova_lm_agesq)]

######Make table of contrasts, rows are names of brain regions that are fdr corrected, columns are contrasts, values are pvalues

#contrast names, -1 = controls, 1-3 are clusters
contrast_names <- c("-1 - 1", "-1 - 2", "-1 - 3", "1 - 2", "1 - 3", "2 - 3")
#go through each fdr corrected brain region, and extract p values
contrast_table <- lapply(volume_emmpairs_lm_agesq_AG_matched_FDR_corrected, function(x) {round(summary(x)$p.value,3)})
#get the names of the brain regions that were fdr corrected
fdr_corrected_brain_regions <- names(contrast_table)
#build table that will hold the name of the brain region and the p values
pairwise_table <- data.frame(matrix(nrow = length(fdr_corrected_brain_regions), ncol = 6))
#give the appropriate names
rownames(pairwise_table) <- fdr_corrected_brain_regions
colnames(pairwise_table) <- contrast_names

#loop through each brain region, and manually assign the columns to be the p values
for (region in fdr_corrected_brain_regions)
{
  pair_pval <- contrast_table[[region]]
  pairwise_table[region,] <- pair_pval
}

#get the mprage out of the name
fdr_corrected_brain_regions_gsub <- gsub("mprage_jlf_vol_", "", fdr_corrected_brain_regions)
fdr_corrected_brain_regions_gsub <- gsub("Cerebell", "Crbl", fdr_corrected_brain_regions_gsub)
fdr_corrected_brain_regions_gsub <- gsub("White_Matter", "WM", fdr_corrected_brain_regions_gsub)
fdr_corrected_brain_regions_gsub <- gsub("Vermal_Lobules", "Verm_lob", fdr_corrected_brain_regions_gsub)
rownames(pairwise_table) <- fdr_corrected_brain_regions_gsub

#Add FDR correction
pairwise_table_with_fdr <- pairwise_table
pairwise_table_with_fdr$p_FDR_corr <- volume_names_and_fdr_values_anova_lm_agesq$p_FDR_corr

#print values
print("LM Agesq pairwise contrasts for FDR corrected values Cortical Volume (MPRAGE JLF)")
print(pairwise_table)

print ("LM Agesq pairwise contrasts and FDR corr Cortical Volume (MPRAGE JLF)")
print(pairwise_table_with_fdr)

sapply(volume_emmpairs_lm_agesq_AG_matched_FDR_corrected, function(x) {print(x)})

#########################################################
#checkmodel with visreg, uncomment when want to check####
#########################################################
invisible(lapply(volume_score_cluster_stats_lm_AG_matched, function(x) {visreg(x)}))

```


