---
title: "Cortical_volume_analysis_matched_age_and_sex_imaging_k3"
author: "Erica Baller"
date: "6/22/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(visreg)
library(mgcv)
library(tableone)
library(dplyr)
library(plm)
library(MatchIt)
library(tidyr)
library(ggplot2)
library(reshape)
theme_update(plot.title = element_text(hjust = 0.5))
```

## R Markdown

This script goes through demographics, volume scores, health, and psych summaries, adds clustering information, runs statistics and makes graphs from results.

Part 1 : Read in csv.s
  -This script reads in demographics, volume_scores, health and psych summaries, merges them, removes NAs, codes and separates by depression.

Part 2 : merge with hydra
  -It then merges these documents with hydra output (made in cbica), adding Hydra_k1 through Hydra_k10 columns (which represent the number of clusters)
  -The script reads in 3 different types of groups (matched)

Part 3 : LM
  -The script then runs LM on each cognitive score (volume_measure ~ hydra_group).  
  -There is a test option that does this for all volume measures and all hydra groups, but for the remainder of the analysis, Hydra_k3 was the only classification more deeply explored.

Part 4 : Anova
  -Anovas were also run on the results of the LM of each volume value by cluster.

Part 5 : Graphing
  - Graphs were then made.  
    *For continuous variables(age, medu1), the graphs represent means, with SEM as error bars
    *For categorical variables (race, sex) the graphs are percentages (caucasian, male) per group, with chisq used to calculate significance
  
Part 6 : FDR Correction
  -FDR correction was calculated for each volume measure ANOVA output
  -A table of the results was extracted
  
Part 7 : Demographics tables
  - Demographics tables matched

```{r volume, echo = FALSE}
#######################################################
############ READ IN, MERGE AND SUBSET DATA############
#######################################################

#read in csvs
demographics <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/n9498_demographics_go1_20161212.csv", header = TRUE, sep = ",") #from /data/joy/BBL/projects/ballerDepHeterogen/data/n9498_demographics_go1_20161212.csv
cnb_scores <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/n9498_cnb_zscores_fr_20170202.csv", header = TRUE, sep = ",") #from /data/joy/BBL/projects/ballerDepHeterogen/data/n9498_cnb_zscores_fr_20170202.csv
health <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/n9498_health_20170405.csv", header = TRUE, sep = ",") #from /data/joy/BBL/projects/ballerDepHeterogen/data/n9498_health_20170405.csv
psych_summary <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/n9498_goassess_psych_summary_vars_20131014.csv", header = TRUE, sep = ",") #from /data/joy/BBL/projects/ballerDepHeterogen/data/n9498_goassess_psych_summary_vars_20131014.csv
t1_qa_scores <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/neuroimaging/t1struct/n1601_t1QaData_20170306.csv", header = TRUE, sep = ",") 
jlfvolume_summary <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/neuroimaging/t1struct/n1601_jlfAntsCTIntersectionVol_20170412.csv", header = TRUE, sep = ",") 



#read in Hydra cluster data -> AG (all_gender), M(males), F(females) 
hydra_AG_matched_clusters <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/hydra_output_from_cbica/hydra_matched/matched_imaging_plus_non_imaging/CogData_matched_age_and_sex_n1424_matched_imaging_plus_non_imaging_HydraSubtypes.csv", header = TRUE, sep = ",")

#Coerce hydra values into factor format
hydra_names <- names(hydra_AG_matched_clusters[2:11])
hydra_AG_matched_clusters[hydra_names] <- lapply(hydra_AG_matched_clusters[hydra_names], factor)


############
#prepping and merging 
############

#remove people with NA for race, age, or sex.  START WITH N = 9498
demographics_noNA_race <- demographics[!is.na(demographics$race),] #everyone has a race, N = 9498
demographics_noNA_race_age <- demographics_noNA_race[!is.na(demographics_noNA_race$ageAtClinicalAssess1),] # 86 people do not have age at clinical assessment.  N = 9412
demographics_noNA_race_age_sex <- demographics_noNA_race_age[!is.na(demographics_noNA_race_age$sex),] #everyone has a sex, N = 9412
demographics_noNA_race_age_andCNBage_sex <- demographics_noNA_race_age_sex[!is.na(demographics_noNA_race_age_sex$ageAtCnb1),] #6 people do not have ageAtCnb1, N = 9406

#remove people with NA for depression or total psych score, START WITH N = 9498
psych_summary_no_NA_dep <- psych_summary[!is.na(psych_summary$smry_dep),] #take out those with NA for depression, 87 people N = 9411
psych_summary_no_NA_dep_and_smry_psych_overall <- psych_summary_no_NA_dep[!is.na(psych_summary_no_NA_dep$smry_psych_overall_rtg),] #take out those with NA for overall psych rtg, no additional people lost, N = 9411

#remove people with excluded imaging

t1_struct_include = subset.data.frame(t1_qa_scores, (t1Exclude == 0))

#merge demographics and imaging #this is if we want to include people without full demographic data
dem_cnb <- merge(demographics_noNA_race_age_andCNBage_sex, cnb_scores, by = "bblid") #merge demographics and cnb, N = 9406
psych_health <- merge(psych_summary_no_NA_dep_and_smry_psych_overall, health, by = "bblid") #merge psych and health, N = 9411
dem_cnb_psych_health <- merge(dem_cnb, psych_health, by = "bblid") #merge all 4 csvs, lost 1 person [134716] (had demographics, but no psych ratings): N = 9405
t1_qa_and_jlfvolume = merge(t1_struct_include, jlfvolume_summary, by = "bblid")

dem_psych_health_qa_volume_merged <- merge (dem_cnb_psych_health, t1_qa_and_jlfvolume, by = "bblid") 
#dem_cnb_psych_health_factor_scores_merged <- merge(dem_cnb_psych_health_merged, cnb_factor_scores, by = "bblid")

#make subsets
subset_just_dep_and_no_medicalratingExclude <- subset.data.frame(dem_psych_health_qa_volume_merged, (medicalratingExclude == 0) & (smry_dep == 4), select = "bblid") 
subset_no_psych_no_medicalratingExclude <- subset.data.frame(dem_psych_health_qa_volume_merged, (medicalratingExclude == 0) & (smry_psych_overall_rtg < 4), select = "bblid") 
subset_dep_or_no_psych_and_no_medicalratingExclude <- subset.data.frame(dem_psych_health_qa_volume_merged, (medicalratingExclude == 0) & ((smry_dep == 4) | (smry_psych_overall_rtg <4))) 

#would binarize depression smry score to -1 (less than 4, not depressed) and 1 (score 4 , depressed)
dep_binarized <- ifelse(subset_dep_or_no_psych_and_no_medicalratingExclude$smry_dep == 4, 1, -1)
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED <- cbind(subset_dep_or_no_psych_and_no_medicalratingExclude, dep_binarized) #N = 3284

#make depression and gender into factor scores
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$dep_binarized <- as.factor(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$dep_binarized)
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$sex <- as.factor(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$sex)

#divide ageAtCNB by 12 for age
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$age_in_years <- subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$ageAtCnb1/12

#race binarized for plotting purposes, caucasian 1, non-caucasion 0
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$race_binarized <- ifelse(as.factor(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED$race) == 1, 1, 0)

#remove people with NA in their cognitive measures
subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED <- subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED[complete.cases(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED[14:39]),]

################################################
### Merge clustering data with subsetted data ##
################################################

#AG (all gender), M (males), F (females) 
#AG Matched - n 1424

subset_with_clusters_AG_matched <- merge(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED, hydra_AG_matched_clusters, by = "bblid")



```

##Demographics

```{r Demographics, echo = FALSE}
#############################
####### Demographics ########
#############################

#######Matched group all clusters ##############
#subset demographics
listVars <- c("Race", "Sex", "Maternal Ed", "Age", "Depression", "Cluster") #Race 1 = caucasian, Maternal Ed = years, age = years, dep 1 = dep, 0 = non_dep
demo_Hydra_k3_AG_matched <- data.frame(subset_with_clusters_AG_matched$race_binarized, subset_with_clusters_AG_matched$sex, subset_with_clusters_AG_matched$medu1, subset_with_clusters_AG_matched$age_in_years, subset_with_clusters_AG_matched$dep_binarized, subset_with_clusters_AG_matched$Hydra_k3)
names(demo_Hydra_k3_AG_matched) <- c(listVars)

#Change categorical values to have names
demo_Hydra_k3_AG_matched$Depression <- ifelse(demo_Hydra_k3_AG_matched$Depression == 1, "Depressed", "Non-depressed")
demo_Hydra_k3_AG_matched$Race <- ifelse(demo_Hydra_k3_AG_matched$Race == 1, "Caucasian", "Non-caucasian")
demo_Hydra_k3_AG_matched$Sex <- ifelse(demo_Hydra_k3_AG_matched$Sex == 1, "Male", "Female")

#Define Categorical Variables
cat_variables <- c("Race", "Depression", "Sex", "Cluster")
title <- c("Hydra_k3 demographics")

#create demographics table
demo_Hydra_k3_AG_matched_table <- CreateTableOne(vars = listVars, data = demo_Hydra_k3_AG_matched, factorVars = cat_variables, strata = c("Cluster"))
print(demo_Hydra_k3_AG_matched_table, showAllLevels = TRUE)



```


```{r Graphs by cluster, echo=FALSE}

#######Chi-square for males/females and race########
##########By males, and by caucasians ##############

#Chi squared sex - significance p = ***
#if just want to look at clusters, not TD, look at commented line below, otherwise keep as is
###chisq_matched_sex <- chisq.test(subset_with_clusters_AG_matched$sex, (subset_with_clusters_AG_matched$Hydra_k3 != -1))
chisq_matched_sex <- chisq.test(subset_with_clusters_AG_matched$sex, subset_with_clusters_AG_matched$Hydra_k3)
chisq_matched_sex_pvalue <- chisq_matched_sex$p.value
total_people_Hydra_k3 <- c(length(subset_with_clusters_AG_matched$sex[which(subset_with_clusters_AG_matched$Hydra_k3 == -1)]), 
                           length(subset_with_clusters_AG_matched$sex[which(subset_with_clusters_AG_matched$Hydra_k3 == 1)]), 
                           length(subset_with_clusters_AG_matched$sex[which(subset_with_clusters_AG_matched$Hydra_k3 == 2)]), 
                           length(subset_with_clusters_AG_matched$sex[which(subset_with_clusters_AG_matched$Hydra_k3 == 3)]))

num_men_all_clusters <- c(length(subset_with_clusters_AG_matched$sex[which(subset_with_clusters_AG_matched$Hydra_k3 == -1 & subset_with_clusters_AG_matched$sex == 1)]), 
                          length(subset_with_clusters_AG_matched$sex[which(subset_with_clusters_AG_matched$Hydra_k3 == 1 & subset_with_clusters_AG_matched$sex == 1)]), 
                          length(subset_with_clusters_AG_matched$sex[which(subset_with_clusters_AG_matched$Hydra_k3 == 2 & subset_with_clusters_AG_matched$sex == 1)]),
                          length(subset_with_clusters_AG_matched$sex[which(subset_with_clusters_AG_matched$Hydra_k3 == 3 & subset_with_clusters_AG_matched$sex == 1)]))
percent_men_all_clusters <- (num_men_all_clusters/total_people_Hydra_k3) * 100


#Chi square race - p-value = 4.85 x 10-13
chisq_matched_race <- chisq.test(subset_with_clusters_AG_matched$race_binarized, subset_with_clusters_AG_matched$Hydra_k3)
chisq_matched_race_pvalue <- chisq_matched_race$p.value
num_caucasian_all_clusters <- c(length(subset_with_clusters_AG_matched$race_binarized[which(subset_with_clusters_AG_matched$Hydra_k3 == -1 & subset_with_clusters_AG_matched$race_binarized == 1)]), 
                                length(subset_with_clusters_AG_matched$race_binarized[which(subset_with_clusters_AG_matched$Hydra_k3 == 1 & subset_with_clusters_AG_matched$race_binarized == 1)]), 
                                length(subset_with_clusters_AG_matched$race_binarized[which(subset_with_clusters_AG_matched$Hydra_k3 == 2 & subset_with_clusters_AG_matched$race_binarized == 1)]),
                                length(subset_with_clusters_AG_matched$race_binarized[which(subset_with_clusters_AG_matched$Hydra_k3 == 3 & subset_with_clusters_AG_matched$race_binarized == 1)]))
percent_caucasian_all_clusters <- (num_caucasian_all_clusters/total_people_Hydra_k3)*100

p_values <- c("", chisq_matched_sex_pvalue, "", chisq_matched_race_pvalue)
dat_sex_race <- data.frame(cl = c("TD", "Cluster1", "Cluster2", "Cluster3", "Significance"), 
                           num_males = c(num_men_all_clusters, "---"),
                           percent_males = round(c(percent_men_all_clusters, chisq_matched_sex_pvalue), 2), 
                           num_caucasians = c(num_caucasian_all_clusters, "---"),
                           percent_caucasian = round(c(percent_caucasian_all_clusters, chisq_matched_race_pvalue),2))
dat_sex_race_no_significance <-  data.frame(cl = c("TD", "Cluster1", "Cluster2", "Cluster3"), 
                                            num_males = (num_men_all_clusters),
                                            percent_males = percent_men_all_clusters, 
                                            num_caucasians = num_caucasian_all_clusters,
                                            percent_caucasian = percent_caucasian_all_clusters)                 
percentages <- data.frame(cl=c("TD", "Cluster1", "Cluster2", "Cluster3"), percent_males = percent_men_all_clusters, percent_caucasians = percent_caucasian_all_clusters)
percentages_for_plot <- melt(percentages, id.vars = "cl")
names(percentages_for_plot) <- c("cluster", "group", "percent")

ggplot(data = percentages_for_plot, aes(x = group, y = percent, group = cluster)) + 
  geom_line(aes(color=cluster)) +
  geom_point(aes(color=cluster)) + 
  ggtitle("Hydra_k3 Percentages")

ggplot(dat_sex_race_no_significance, aes(x = cl, y = percent_males, fill=cl)) + geom_col() +
  scale_x_discrete(limits=c("TD", "Cluster1", "Cluster2", "Cluster3")) + ylim(0, 100) + xlab("Clusters") + ylab("% Male") + 
  ggtitle("Hydra_k3 % Male, p = ***") + scale_fill_discrete(breaks=c("TD", "Cluster1", "Cluster2", "Cluster3")) +
  guides(fill=guide_legend(title=NULL))
ggplot(dat_sex_race_no_significance, aes(x = cl, y = percent_caucasian, fill=cl)) + geom_col() + 
  scale_x_discrete(limits=c("TD", "Cluster1", "Cluster2", "Cluster3")) + ylim(0, 100) + xlab("Clusters") + ylab("% Caucasian") + 
  ggtitle("Hydra_k3 % Caucasian, p = ***") + scale_fill_discrete(breaks=c("TD", "Cluster1", "Cluster2", "Cluster3")) + 
  guides(fill=guide_legend(title=NULL))




#############################
######### Bar Graphs ########
#############################

dat <- data.frame(cluster=c(subset_with_clusters_AG_matched$Hydra_k3), age=c(subset_with_clusters_AG_matched$age_in_years), medu1=c(subset_with_clusters_AG_matched$medu1), race=c(subset_with_clusters_AG_matched$race_binarized), sex_males=c(subset_with_clusters_AG_matched$sex))

dat_age_sd_sem <- data.frame(cl = c("TD", "Cluster1", "Cluster2", "Cluster3"),
                             age = c(mean(subset_with_clusters_AG_matched$age_in_years[which(subset_with_clusters_AG_matched$Hydra_k3 ==-1)]), 
                                     mean(subset_with_clusters_AG_matched$age_in_years[which(subset_with_clusters_AG_matched$Hydra_k3 ==1)]), 
                                     mean(subset_with_clusters_AG_matched$age_in_years[which(subset_with_clusters_AG_matched$Hydra_k3 ==2)]),
                                     mean(subset_with_clusters_AG_matched$age_in_years[which(subset_with_clusters_AG_matched$Hydra_k3 ==3)])),
                             age_sd = c(sd(subset_with_clusters_AG_matched$age_in_years[which(subset_with_clusters_AG_matched$Hydra_k3 ==-1)]),
                                        sd(subset_with_clusters_AG_matched$age_in_years[which(subset_with_clusters_AG_matched$Hydra_k3 ==1)]), 
                                        sd(subset_with_clusters_AG_matched$age_in_years[which(subset_with_clusters_AG_matched$Hydra_k3 ==2)]),
                                        sd(subset_with_clusters_AG_matched$age_in_years[which(subset_with_clusters_AG_matched$Hydra_k3 ==3)])))

dat_age_sd_sem$sem <- dat_age_sd_sem$age_sd/sqrt(nrow(dat)) 
dat_medu_sd_sem <- data.frame(cl = c("TD", "Cluster1", "Cluster2", "Cluster3"), 
                              medu = c(mean(subset_with_clusters_AG_matched$medu1[which(subset_with_clusters_AG_matched$Hydra_k3 ==-1)]),
                                       mean(subset_with_clusters_AG_matched$medu1[which(subset_with_clusters_AG_matched$Hydra_k3 ==1)]), 
                                       mean(subset_with_clusters_AG_matched$medu1[which(subset_with_clusters_AG_matched$Hydra_k3 ==2)]),
                                       mean(subset_with_clusters_AG_matched$medu1[which(subset_with_clusters_AG_matched$Hydra_k3 ==3)])), 
                              medu_sd = c(sd(subset_with_clusters_AG_matched$medu1[which(subset_with_clusters_AG_matched$Hydra_k3 ==-1)]), 
                                         sd(subset_with_clusters_AG_matched$medu1[which(subset_with_clusters_AG_matched$Hydra_k3 ==1)]), 
                                         sd(subset_with_clusters_AG_matched$medu1[which(subset_with_clusters_AG_matched$Hydra_k3 ==2)]),
                                         sd(subset_with_clusters_AG_matched$medu1[which(subset_with_clusters_AG_matched$Hydra_k3 ==3)])))
                                      

dat_medu_sd_sem$sem <- dat_medu_sd_sem$medu_sd/sqrt(nrow(dat))
dat_age_medu_sem_melted <- melt(c(dat_age_sd_sem$sem,dat_medu_sd_sem$sem), id.vars = "cl")

age = c(mean(subset_with_clusters_AG_matched$age_in_years[which(subset_with_clusters_AG_matched$Hydra_k3 ==-1)]), 
        mean(subset_with_clusters_AG_matched$age_in_years[which(subset_with_clusters_AG_matched$Hydra_k3 ==1)]), 
        mean(subset_with_clusters_AG_matched$age_in_years[which(subset_with_clusters_AG_matched$Hydra_k3 ==2)]),
        mean(subset_with_clusters_AG_matched$age_in_years[which(subset_with_clusters_AG_matched$Hydra_k3 ==3)]))

medu = c(mean(subset_with_clusters_AG_matched$medu1[which(subset_with_clusters_AG_matched$Hydra_k3 ==-1)]),
         mean(subset_with_clusters_AG_matched$medu1[which(subset_with_clusters_AG_matched$Hydra_k3 ==1)]), 
         mean(subset_with_clusters_AG_matched$medu1[which(subset_with_clusters_AG_matched$Hydra_k3 ==2)]),
         mean(subset_with_clusters_AG_matched$medu1[which(subset_with_clusters_AG_matched$Hydra_k3 ==3)]))

#get everything into the right format
age_and_medu <- data.frame(cl=c("TD", "Cluster1", "Cluster2", "Cluster3"), age = age, medu = medu)
dat_age_medu_sem_melted <- melt(c(dat_age_sd_sem$sem,dat_medu_sd_sem$sem), id.vars = "cl")
age_and_medu_for_plot <- melt(age_and_medu, id.vars = "cl")
age_and_medu_for_plot$sem <- dat_age_medu_sem_melted
names(age_and_medu_for_plot) <- c("cluster", "group", "years", "sem")

ggplot(data = age_and_medu_for_plot, aes(x = group, y = years, group = cluster)) + 
  geom_line(aes(color=cluster)) +
  geom_point(aes(color=cluster)) + 
  geom_errorbar(aes(ymin=years-sem, ymax=years+sem), width=.1) +
  ggtitle("Hydra_k3 Ages")

ggplot(dat_age_sd_sem, aes(x = cl, y = age, fill = cl)) + geom_col() + 
  geom_errorbar(aes(ymin=age-sem, ymax=age+sem),width=.2,position=position_dodge(.9)) + 
  scale_x_discrete(limits=c("TD", "Cluster1", "Cluster2", "Cluster3")) + ylim(0, 18) + xlab("Clusters") + ylab("Age in Years") + 
  ggtitle("Age by Cluster") + scale_fill_discrete(breaks=c("TD", "Cluster1", "Cluster2", "Cluster3")) +
    guides(fill=guide_legend(title=NULL)) 

ggplot(dat_medu_sd_sem, aes(x = cl, y = medu, fill = cl)) + geom_col() + 
  geom_errorbar(aes(ymin=medu-sem, ymax=medu+sem),width=.2,position=position_dodge(.9)) + 
  scale_x_discrete(limits=c("TD", "Cluster1", "Cluster2", "Cluster3")) + ylim(0, 18) + xlab("Clusters") + ylab("Maternal Ed in Years") + 
  ggtitle("Maternal Edu by Cluster") + scale_fill_discrete(breaks=c("TD", "Cluster1", "Cluster2", "Cluster3")) +
  guides(fill=guide_legend(title=NULL)) 



```

```{r stats, echo = TRUE}
#################################
# Linear Model for each measure #
##### Results stored in list ####
#################################

#get volume measure names
volume_measure_names <- names(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED)[grep("_vol_", names(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED))] #get the names of all the columns with _vol in the name
cluster_names <- colnames(hydra_AG_matched_clusters[,2:11])

volume_measure_names_list <- names(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED)[grep("_vol_", names(subset_dep_or_no_psych_and_no_medicalratingExclude_DEPBINARIZED))] #get the names of all the columns with _vol_ in the name
cluster_names_list <- colnames(hydra_AG_matched_clusters[,2:11])

#### All Hydra clusters in embedded lis t######
#lm
volume_cog_score_cluster_stats_lm_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
  volume_cog_score_cluster_stats_lm_AG_matched_withincluster<- lapply(volume_measure_names_list, cluster=as.name(cluster_name), function(volume_measure_name, cluster) 
  {
    volume_measure <- as.name(volume_measure_name)
    lm(substitute(volume_measure ~ cluster, list(volume_measure = volume_measure, cluster = cluster)), data = subset_with_clusters_AG_matched)
  })
  setNames(volume_cog_score_cluster_stats_lm_AG_matched_withincluster, volume_measure_names_list)
})
names(volume_cog_score_cluster_stats_lm_AG_matched_by_cluster_1through10) <- cluster_names_list

#gam
volume_cog_score_cluster_stats_gam_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
 volume_cog_score_cluster_stats_gam_AG_matched_withincluster<- lapply(volume_measure_names_list, cluster=as.name(cluster_name),   function(volume_measure_name, cluster) 
 {
    volume_measure <- as.name(volume_measure_name)
    gam(substitute(volume_measure ~ cluster + sex + s(age_in_years) + averageManualRating, list(volume_measure = volume_measure, cluster = cluster)), data = subset_with_clusters_AG_matched)
  })
 setNames(volume_cog_score_cluster_stats_gam_AG_matched_withincluster, volume_measure_names_list)
})
names(volume_cog_score_cluster_stats_gam_AG_matched_by_cluster_1through10) <- cluster_names_list

##### Just Hydra_3 clusters ######
#lm
volume_cog_score_cluster_stats_lm_AG_matched <- lapply(volume_measure_names, function(x) 
{
  lm(substitute(i ~ Hydra_k3, list(i = as.name(x))), data = subset_with_clusters_AG_matched)
})
names(volume_cog_score_cluster_stats_lm_AG_matched) <- volume_measure_names

#gam
volume_cog_score_cluster_stats_gam_AG_matched <- lapply(volume_measure_names, function(x) 
{
  volume_measure = as.name(x)
  gam(substitute(volume_measure ~ Hydra_k3 + sex + s(age_in_years) + averageManualRating, list(volume_measure = volume_measure)), data = subset_with_clusters_AG_matched)
})
names(volume_cog_score_cluster_stats_gam_AG_matched) <- volume_measure_names

##############################
####### Statistics ###########
##############################

######## All hydra clusters, Anova results ########
#lm anova all clusters
volume_cog_score_cluster_stats_anova_lm_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
  volume_cog_score_cluster_stats_anova_AG_withincluster <- lapply(volume_measure_names_list, cluster=as.name(cluster_name), function(volume_measure_name, cluster) 
  {
     volume_measure <- as.name(volume_measure_name)
     anova(lm(substitute(volume_measure ~ cluster, list(volume_measure = volume_measure, cluster = cluster)), data = subset_with_clusters_AG_matched))
  })
  setNames(volume_cog_score_cluster_stats_anova_AG_withincluster, volume_measure_names_list)
})
names(volume_cog_score_cluster_stats_anova_lm_AG_matched_by_cluster_1through10) <- cluster_names_list

#gam anova all clusters
volume_cog_score_cluster_stats_anova_gam_AG_matched_by_cluster_1through10 <- lapply(cluster_names_list, function(cluster_name)
{
  volume_cog_score_cluster_stats_anova_gam_AG_withincluster <- lapply(volume_measure_names_list, cluster=as.name(cluster_name), function(volume_measure_name, cluster) 
  {
     volume_measure <- as.name(volume_measure_name)
     anova(gam(substitute(volume_measure ~ cluster + sex + s(age_in_years) + averageManualRating, list(volume_measure = volume_measure, cluster = cluster)), data = subset_with_clusters_AG_matched))
  })
  setNames(volume_cog_score_cluster_stats_anova_gam_AG_withincluster, volume_measure_names_list)
})
names(volume_cog_score_cluster_stats_anova_gam_AG_matched_by_cluster_1through10) <- cluster_names_list

#####Just Hydra 3 clusters ANOVA ########
#lm Hydra K3 Anova
volume_cog_score_cluster_stats_anova_lm_AG_matched <- lapply(volume_cog_score_cluster_stats_lm_AG_matched, anova) 
names(volume_cog_score_cluster_stats_anova_lm_AG_matched) <- volume_measure_names

#gam Hydra K3 ANOVA
volume_cog_score_cluster_stats_anova_gam_AG_matched <- lapply(volume_cog_score_cluster_stats_gam_AG_matched, anova)
names(volume_cog_score_cluster_stats_anova_gam_AG_matched) <- volume_measure_names


```

##Results graphically presented
```{r Results graphically presented, echo = FALSE}


#####################################
###### By volume Measure ###############
#####################################
#can do with all gender as well, as well as matched/unmatched, etc
#loop through each cluster and each volume measure, make text and evaluate the following: mean of each cluster by measure, and sd of each cluster by measure
#SEM calculated by taking SD, and dividing by the square root of the number of people in the analysis... Should this be by # people in cluster?


groups_list <- data.frame(cbind(c("TD", "Cluster1", "Cluster2", "Cluster3"), c("-1", "1", "2", "3")))
names(groups_list) <- c("cl", "numeric")
all_mean_sd_sem <- data.frame(rep(groups_list$cl, 129), rep(volume_measure_names, each = 4), rep(0, 1), rep(0, 1), rep(0,1))
names(all_mean_sd_sem) <- c("cl", "volume", "mean", "sd", "sem")
for(volume in volume_measure_names_list){
  for(num in 1:4) {
    clst <- groups_list[num,1]
    meas <- groups_list[num,2]
    mean_for_eval <- paste("mean(subset_with_clusters_AG_matched$", volume, "[which(subset_with_clusters_AG_matched$Hydra_k3 == ", groups_list[num,2], ")])", sep="")
    mean_grp <- eval(parse(text=as.name(mean_for_eval)))
    all_mean_sd_sem$mean[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$volume == volume)] <- mean_grp
    
    sd_for_eval <- paste("sd(subset_with_clusters_AG_matched$", volume, "[which(subset_with_clusters_AG_matched$Hydra_k3 == ", groups_list[num,2], ")])", sep="")
    sd_grp <- eval(parse(text=as.name(sd_for_eval)))
    all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$volume == volume)] <- sd_grp
    all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$volume == volume)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$volume == volume)]/sqrt(nrow(subset_with_clusters_AG_matched))
  }
}


#add sems to volume_measures_for_plot
#volume_measures_for_plot$sem <- all_sem_one_col
#names(volume_measures_for_plot) <- c("cluster", "volume", "z_score", "sem")
ggplot(data = all_mean_sd_sem, aes(x = volume, y = mean, group = cl)) +  ylab("Mean Volume") +
  geom_line(aes(color=cl)) +
  geom_point(aes(color=cl)) + 
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.1) +
  ggtitle("Hydra_k3 by volume Measures")

```

FDR correction 
```{r FDR Correction, echo = FALSE}

###################################################
## Extracting anovas with significant p values ####
###################################################
#lm
#Looking at Hydra_k3, but can redo with nested list
#Look at model summaries
models_anova <- lapply(volume_cog_score_cluster_stats_anova_lm_AG_matched, summary)

#Pull p-values
p_anova <- sapply(volume_cog_score_cluster_stats_anova_lm_AG_matched, function(v) v$"Pr(>F)"[1]) #$coef[,"Pr(>F)"][2]) #get the p value for dep binarized

#Convert to data frame
p_anova <- as.data.frame(p_anova)

#Print original p-values to three decimal places
p_round_anova <- round(p_anova,3)

#FDR correct p-values
pfdr_anova <- p.adjust(p_anova[,1],method="fdr")

#Convert to data frame
pfdr_anova <- as.data.frame(pfdr_anova)
row.names(pfdr_anova) <- volume_measure_names

#To print fdr-corrected p-values to three decimal places
pfdr_round_anova <- round(pfdr_anova,3)

#List the NMF components that survive FDR correction
volume_fdr_anova <- row.names(pfdr_anova)[pfdr_anova<0.05]

#make a data frame with names and fdr values (rounded to 3 decimals)
volume_names_and_fdr_values_anova <- data.frame(cbind(volume_fdr_anova, round(pfdr_anova[pfdr_anova<0.05],3)))

#add titles to names_and_fdr tables
names(volume_names_and_fdr_values_anova) <- c("volume_measure", "p_FDR_corr")

print("LM")
print(volume_names_and_fdr_values_anova)



#gam

#Looking at Hydra_k3, but can redo with nested list
#Look at model summaries
#models_anova <- lapply(volume_cog_score_cluster_stats_anova_gam_AG_matched, summary)

#Pull p-values
p_anova <- sapply(volume_cog_score_cluster_stats_anova_gam_AG_matched, function(v) v$pTerms.table[1,3])
                    #"Pr(>F)"[1]) #$coef[,"Pr(>F)"][2]) #get the p value for dep binarized

#Convert to data frame
p_anova <- as.data.frame(p_anova)

#Print original p-values to three decimal places
p_round_anova <- round(p_anova,3)

#FDR correct p-values
pfdr_anova <- p.adjust(p_anova[,1],method="fdr")

#Convert to data frame
pfdr_anova <- as.data.frame(pfdr_anova)
row.names(pfdr_anova) <- volume_measure_names

#To print fdr-corrected p-values to three decimal places
pfdr_round_anova <- round(pfdr_anova,3)

#List the NMF components that survive FDR correction
volume_fdr_anova <- row.names(pfdr_anova)[pfdr_anova<0.05]

#make a data frame with names and fdr values (rounded to 3 decimals)
volume_names_and_fdr_values_anova <- data.frame(cbind(volume_fdr_anova, round(pfdr_anova[pfdr_anova<0.05],3)))

#add titles to names_and_fdr tables
names(volume_names_and_fdr_values_anova) <- c("volume_measure", "p_FDR_corr_GAM")

print("GAM")
print(volume_names_and_fdr_values_anova)

#checkmodel with visreg, uncomment when want to check
invisible(lapply(volume_cog_score_cluster_stats_lm_AG_matched, function(x) {visreg(x)}))

```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
