---
title: "FC Task active/DMN, matched age and sex, n312, Hydra K3, 27 jneurosci labels, 2mm"
author: "Erica Baller"
date: "2/5/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 9)
library(visreg)
library(mgcv)
library(tableone)
library(dplyr)
library(plm)
library(MatchIt)
library(tidyr)
library(ggplot2)
library(reshape)
library(emmeans)
library(MASS)
require(cowplot)
theme_update(plot.title = element_text(hjust = 0.5))
source("~/BBL/from_chead/ballerDepHeterogen/ballerDepHeterogenScripts/Hydra_functions.R")

```

## R Markdown

This script goes through demographics, network scores, health, and psych summaries, adds clustering information, runs statistics and makes graphs from results.

When changing things- change the file path, the network range to grab names from, and the number of clusters

Part 1 : Read in csv with network data, demographics, health and psych summaries, and depression scores (this file was made from PrepForNetworks 20180706.csv and sent to chead, where network data was calculated with cedric's scripts)

Part 2 : Demographics tables
  - Demographics tables matched
  
Part 3 : Graphing
  - Graphs were then made.  
    *For continuous variables(age, medu1), the graphs represent means, with SEM as error bars
    *For categorical variables (race, sex) the graphs are percentages (caucasian, male) per group, with chisq used to calculate significance

Part 4 : LM/GAM/LM with Agesq
  -The script then runs LM on each cognitive score (network ~ hydra_group). 
   - Does gam (network ~ hydra_group + s(age) + sex + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion)
   - Does LM with ageSq (network ~ hydra_group + ageSq + sex + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion)
  -There is a test option that does this for all network measures and all hydra groups, but for the remainder of the analysis, Hydra_k3 was the only classification more deeply explored.

Part 5 : Anovas
  -Anovas were also run on the results of the LM of each network value by cluster.


Part 6 : FDR Correction
  -FDR correction was calculated for each network measure ANOVA output
  -A table of the results was extracted
  


```{r connectivity, echo = FALSE}
#######################################################
############ READ IN, MERGE AND SUBSET DATA############
#######################################################

#read in csvs, CHANGE THINGS HERE

num_communities <- 2
num_clusters <- 3
#exclusion <- "weighted"

#data has the OLD files, that were not pearson correlated correctly
#filename <- Sys.glob(paste0("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/output_of_fc/concatenate_rest_nback_idemo/fc_concat_", exclusion, "_r", res, "_com", num_communities, "/fc_concat_", exclusion, "_r", res, "_com", num_communities, ".csv"))

filename <- Sys.glob(paste0("/Users/eballer/BBL/from_chead/ballerDepHeterogen/results/csvs/fc_27roi_20190130_2mm.csv"))
#, exclusion, "_r", res, "_com", num_communities, "/fc_concat_", exclusion, "_r", res, "_com", num_communities, ".csv"))

rest_QA <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/neuroimaging/rest/n1601_RestQAData_20170714.csv")
nback_QA <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/neuroimaging/nback/n1601_NbackConnectQAData_20170718.csv")
idemo_QA <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/neuroimaging/idemo/n1601_idemo_FinalQA_092817.csv")

fc_networks_and_dem_clinical_psych_data <- read.csv(filename)

#fc_networks_and_dem_clinical_psych_data <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/output_of_fc/fc_r400_com17/fc_r400_com17.csv")

#subset_with_clusters_AG_matched - rename because this is what will be used for the rest of the script
subset_with_clusters_AG_matched <- fc_networks_and_dem_clinical_psych_data

#Get cluster and network names
clusters <- names(fc_networks_and_dem_clinical_psych_data[grep ("Hydra", names(fc_networks_and_dem_clinical_psych_data))])
num_fc_pairs <- (num_communities * (num_communities -1))/2 + num_communities
networks <- names(subset_with_clusters_AG_matched[2:(num_fc_pairs+1)])


####New as of 10/21/2018 ####
#read in new hydra clusters
new_hydra_clusters <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/hydra_output_from_cbica/hydra_matched/20181121_OLD_HYDRA_with_new_script_from_toni/CogData_age_and_sex_n1424_matched_imaging_plus_non_imaging_replication_20181121_HydraSubtypes.csv", header = TRUE, sep = ",")

# remove old hydra clusters
subset_with_clusters_AG_matched <- subset_with_clusters_AG_matched[, !(colnames(subset_with_clusters_AG_matched) %in% c(clusters))]

#add new hydra clusters 
subset_with_clusters_AG_matched <- merge(subset_with_clusters_AG_matched, new_hydra_clusters, by = "bblid")

#merge with the QA measures
subset_with_clusters_AG_matched <- merge(subset_with_clusters_AG_matched, rest_QA, by = c("bblid", "scanid"))
subset_with_clusters_AG_matched <- merge(subset_with_clusters_AG_matched, nback_QA, by = c("bblid", "scanid"))
subset_with_clusters_AG_matched <- merge(subset_with_clusters_AG_matched, idemo_QA, by = c("bblid", "scanid"))

subset_with_clusters_AG_matched$ageSq <- as.numeric(I(scale(subset_with_clusters_AG_matched$age_in_years, scale = FALSE, center = TRUE)^2))
subset_with_clusters_AG_matched$dep_binarized <- subset_with_clusters_AG_matched$Hydra_k1

#set up within/between networks
within <- c("Task_active_Task_active", "Default_mode_Default_mode")
#within <- c("visual_visual", "somatomotor_somatomotor", "dorsalAttention_dorsalAttention", "salienceVentralAttention_salienceVentralAttention", "limbic_limbic", "frontoparietalControl_frontoparietalControl", "default_default")
between <- networks[!is.element(networks, within)]

#Coerce hydra values into factor format
#fc_networks_and_dem_clinical_psych_data[clusters] <- lapply(fc_networks_and_dem_clinical_psych_data[clusters], factor)
subset_with_clusters_AG_matched[clusters] <- lapply(subset_with_clusters_AG_matched[clusters], factor)

subset_with_clusters_AG_matched_noTD <-eval(parse(text=as.name(paste0("subset_with_clusters_AG_matched[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " != -1),]"))))

#get number of measures (to be used later on when trying to make graphs), for every different modality WILL HAVE TO CHANGE THIS
num_measures <- length(networks)
num_within <- length(within)
num_between<- num_measures - num_within
#get cluster titles 

cluster_titles <- get_cluster_titles(hydra_cluster = num_clusters)
```



```{r Graphs by cluster, echo=FALSE}

#######Chi-square for males/females and race########
##########By males, and by caucasians ##############



#Chi squared 
chisq_matched_sex <- chi_sq(data_frame = subset_with_clusters_AG_matched, "sex", num_clusters)
chisq_matched_race <- chi_sq(data_frame = subset_with_clusters_AG_matched, "race_binarized", num_clusters)

#get means/stds
total_people_Hydra <- total_people_per_cluster(data_frame = subset_with_clusters_AG_matched, hydra_cluster = num_clusters)

num_men_all_clusters <- total_people_per_cluster_by_group(data_frame = subset_with_clusters_AG_matched, variable = "sex", hydra_cluster = num_clusters, group_val = 1)
num_caucasian_all_clusters <- total_people_per_cluster_by_group(data_frame = subset_with_clusters_AG_matched, variable = "race_binarized", hydra_cluster = num_clusters, group_val = 1)

percent_men_all_clusters <- (num_men_all_clusters/total_people_Hydra) * 100
percent_caucasian_all_clusters <- (num_caucasian_all_clusters/total_people_Hydra)*100

p_values <- c("", chisq_matched_sex$p.value, "", chisq_matched_race$p.value)

dat_sex_race <- data.frame(cl = c(cluster_titles, "Significance"), 
                           num_males = c(num_men_all_clusters, "---"),
                           percent_males = round(c(percent_men_all_clusters, chisq_matched_sex$p.value), 2), 
                           num_caucasians = c(num_caucasian_all_clusters, "---"),
                           percent_caucasian = round(c(percent_caucasian_all_clusters, chisq_matched_race$p.value),2))
dat_sex_race_no_significance <-  data.frame(cl = cluster_titles, 
                                            num_males = (num_men_all_clusters),
                                            percent_males = percent_men_all_clusters, 
                                            num_caucasians = num_caucasian_all_clusters,
                                            percent_caucasian = percent_caucasian_all_clusters)                 
percentages <- data.frame(cl=cluster_titles, percent_males = percent_men_all_clusters, percent_caucasians = percent_caucasian_all_clusters)
percentages_for_plot <- melt(percentages, id.vars = "cl")
names(percentages_for_plot) <- c("cluster", "group", "percent")

#Set Titles for plots
title1 <- paste0("Hydra_k", num_clusters, " Percentages")

if(chisq_matched_sex$p.value < 0.05) {
  title2 <- paste0("Hydra_k", num_clusters, "% Male, p < 0.05")
} else {
  title2 <- paste0("Hydra_k", num_clusters, "% Male, p = ", round(chisq_matched_sex$p.value, 2))
}

if(chisq_matched_race$p.value < 0.05) {
  title3 <- paste0("Hydra_k", num_clusters, "% Caucasian, p < 0.05")
} else {
  title3 <- paste0("Hydra_k", num_clusters, "% Caucasian, p = ", round(chisq_matched_race$p.value, 2))
}

#plot
ggplot(data = percentages_for_plot, aes(x = group, y = percent, group = cluster)) + 
  geom_line(aes(color=cluster)) +
  geom_point(aes(color=cluster)) + 
  ggtitle(title1)

ggplot(dat_sex_race_no_significance, aes(x = cl, y = percent_males, fill=cl)) + geom_col() +
  scale_x_discrete(limits=cluster_titles) + ylim(0, 100) + xlab("Clusters") + ylab("% Male") + 
  ggtitle(title2) + scale_fill_discrete(breaks=cluster_titles) +
  guides(fill=guide_legend(title=NULL))

ggplot(dat_sex_race_no_significance, aes(x = cl, y = percent_caucasian, fill=cl)) + geom_col() + 
  scale_x_discrete(limits=cluster_titles) + ylim(0, 100) + xlab("Clusters") + ylab("% Caucasian") + 
  ggtitle(title3) + scale_fill_discrete(breaks=cluster_titles) + 
  guides(fill=guide_legend(title=NULL))

#############################
######### Bar Graphs ########
#############################

variable_name_string <- c("age", "medu") #this allows you to specify the actual titles, if different from the data frame titles
plot_list <- plot_continuous_variables(data_frame = subset_with_clusters_AG_matched, var1 = "age_in_years", var2 = "medu1", hydra_cluster = num_clusters, optional_variable_name_string = variable_name_string)
for(x in 1:length(plot_list)){
  print(plot_list[[x]])
}

```

```{r stats, echo = FALSE}
#################################
# Linear Model for each measure #
##### Results stored in list ####
#################################



#### All Hydra clusters in embedded lis t######
network_cluster_stats_lm_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
{
  network_cluster_stats_lm_AG_matched_withincluster<- lapply(networks, cluster=as.name(cluster), function(network, cluster) 
  {
    network <- as.name(network)
    lm(substitute(network ~ cluster + sex + age_in_years + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion, list(network = network, cluster = cluster)), data = subset_with_clusters_AG_matched)
  })
  setNames(network_cluster_stats_lm_AG_matched_withincluster, networks)
})

names(network_cluster_stats_lm_AG_matched_by_cluster_1through10) <- clusters


#gam
network_cluster_stats_gam_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
{
 network_cluster_stats_gam_AG_matched_withincluster<- lapply(networks, cluster=as.name(cluster), function(network, cluster) 
 {
    network <- as.name(network)
    gam(substitute(network ~ cluster + sex + s(age_in_years) + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion, list(network = network, cluster = cluster)), data = subset_with_clusters_AG_matched, method = "REML")
  })
 setNames(network_cluster_stats_gam_AG_matched_withincluster, networks)
})
names(network_cluster_stats_gam_AG_matched_by_cluster_1through10) <- clusters

#LM with mean-centered, squared age- quadratic term#

network_cluster_stats_lm_agesq_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
{
  network_cluster_stats_lm_agesq_AG_matched_withincluster<- lapply(networks, cluster=as.name(cluster), function(network, cluster) 
  {
    network <- as.name(network)
    lm(substitute(network ~ cluster + sex + age_in_years + ageSq + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion, list(network = network, cluster = cluster)), data = subset_with_clusters_AG_matched)
  })
  setNames(network_cluster_stats_lm_agesq_AG_matched_withincluster, networks)
})
names(network_cluster_stats_lm_agesq_AG_matched_by_cluster_1through10) <- clusters


##### Just Hydra_3 clusters ######
#lm
network_cluster_stats_lm_AG_matched <- lapply(networks, function(network) 
{
  lm(substitute(i ~ Hydra_k3 + sex + age_in_years + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion, list(i = as.name(network))), data = subset_with_clusters_AG_matched)
})
names(network_cluster_stats_lm_AG_matched) <- networks

#gam
network_cluster_stats_gam_AG_matched <- lapply(networks, function(network) 
{
  network = as.name(network)
  gam(substitute(network ~ Hydra_k3 + sex + s(age_in_years) + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion, list(network = network)), data = subset_with_clusters_AG_matched, method = "REML")
})
names(network_cluster_stats_gam_AG_matched) <- networks

#lm ageSq and mean centered
network_cluster_stats_lm_agesq_AG_matched <- lapply(networks, function(network) 
{
  lm(substitute(i ~ Hydra_k3 + sex + age_in_years + ageSq + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion, list(i = as.name(network))), data = subset_with_clusters_AG_matched)
})
names(network_cluster_stats_lm_agesq_AG_matched) <- networks


#Just Hydra K3, NO TDs
#lm
network_cluster_stats_lm_AG_matched_noTD <- lapply(networks, function(network) 
{
  lm(substitute(i ~ Hydra_k3 + sex + age_in_years + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion, list(i = as.name(network))), data = subset_with_clusters_AG_matched_noTD)
})
names(network_cluster_stats_lm_AG_matched_noTD) <- networks

#gam
network_cluster_stats_gam_AG_matched_noTD <- lapply(networks, function(network) 
{
  network = as.name(network)
  gam(substitute(network ~ Hydra_k3 + sex + s(age_in_years) + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion, list(network = network)), data = subset_with_clusters_AG_matched_noTD, method = "REML")
})
names(network_cluster_stats_gam_AG_matched_noTD) <- networks

#lm ageSq and mean centered
network_cluster_stats_lm_agesq_AG_matched_noTD <- lapply(networks, function(network) 
{
  lm(substitute(i ~ Hydra_k3 + sex + age_in_years + ageSq + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion, list(i = as.name(network))), data = subset_with_clusters_AG_matched_noTD)
})
names(network_cluster_stats_lm_agesq_AG_matched_noTD) <- networks


##############################
####### Statistics ###########
##############################

######## All hydra clusters, Anova results ########

#lm
network_cluster_stats_anova_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
{
  network_cluster_stats_anova_AG_withincluster <- lapply(networks, cluster=as.name(cluster), function(network, cluster) 
  {
     network <- as.name(network)
     anova(lm(substitute(network ~ cluster + sex + age_in_years + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion, list(network = network, cluster = cluster)), data = subset_with_clusters_AG_matched))
  })
  setNames(network_cluster_stats_anova_AG_withincluster, networks)
})
names(network_cluster_stats_anova_AG_matched_by_cluster_1through10) <- clusters

#gam anova all clusters
network_cluster_stats_anova_gam_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
{
  network_cluster_stats_anova_gam_AG_withincluster <- lapply(networks, cluster=as.name(cluster), function(network, cluster) 
  {
     network <- as.name(network)
     anova(gam(substitute(network ~ cluster + sex + s(age_in_years) + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion, list(network = network, cluster = cluster)), data = subset_with_clusters_AG_matched, method = "REML"))
  })
  setNames(network_cluster_stats_anova_gam_AG_withincluster, networks)
})
names(network_cluster_stats_anova_gam_AG_matched_by_cluster_1through10) <- clusters

#lm agesq anova all clusters
network_cluster_stats_anova_lm_agesq_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
{
  network_cluster_stats_anova_lm_agesq_AG_withincluster <- lapply(networks, cluster=as.name(cluster), function(network, cluster) 
  {
     network <- as.name(network)
     anova(lm(substitute(network ~ cluster + sex + age_in_years + ageSq + restRelMeanRMSMotion + nbackRelMeanRMSMotion + idemoRelMeanRMSMotion, list(network = network, cluster = cluster)), data = subset_with_clusters_AG_matched))
  })
  setNames(network_cluster_stats_anova_lm_agesq_AG_withincluster, networks)
})
names(network_cluster_stats_anova_lm_agesq_AG_matched_by_cluster_1through10) <- clusters


#####Just Hydra 3 clusters ANOVA ########
#lm Hydra K3 Anova
network_cluster_stats_anova_lm_AG_matched <- lapply(network_cluster_stats_lm_AG_matched, anova) 
names(network_cluster_stats_anova_lm_AG_matched) <- networks

#gam Hydra K3 ANOVA
network_cluster_stats_anova_gam_AG_matched <- lapply(network_cluster_stats_gam_AG_matched, anova)
names(network_cluster_stats_anova_gam_AG_matched) <- networks

#lm Hydra K3 Anova
network_cluster_stats_anova_lm_agesq_AG_matched <- lapply(network_cluster_stats_lm_agesq_AG_matched, anova) 
names(network_cluster_stats_anova_lm_agesq_AG_matched) <- networks

#####Just Hydra 3 clusters ANOVA, No TD ########
#lm Hydra K3 Anova
network_cluster_stats_anova_lm_AG_matched_noTD <- lapply(network_cluster_stats_lm_AG_matched_noTD, anova) 
names(network_cluster_stats_anova_lm_AG_matched_noTD) <- networks

#gam Hydra K3 ANOVA
network_cluster_stats_anova_gam_AG_matched_noTD <- lapply(network_cluster_stats_gam_AG_matched_noTD, anova)
names(network_cluster_stats_anova_gam_AG_matched_noTD) <- networks

#lm Hydra K3 Anova
network_cluster_stats_anova_lm_agesq_AG_matched_noTD <- lapply(network_cluster_stats_lm_agesq_AG_matched_noTD, anova) 
names(network_cluster_stats_anova_lm_agesq_AG_matched_noTD) <- networks

```

##Results graphically presented
```{r Results graphically presented, echo = FALSE}


#####################################
###### By FC Connectivity Measure ###############
#####################################
#can do with all gender as well, as well as matched/unmatched, etc
#loop through each cluster and each network measure, make text and evaluate the following: mean of each cluster by measure, and sd of each cluster by measure

cluster_titles <- get_cluster_titles(hydra_cluster = num_clusters)
cluster_vector <- get_cluster_numerical_vector(hydra_cluster = num_clusters)
groups <- data.frame(cbind(cluster_titles, cluster_vector))
names(groups) <- c("cl", "numeric")
total_num_groups <- num_clusters + 1

#construct data frame of names of connectivity groups
df_names <- data.frame(rep(groups$cl, num_measures), rep(networks, each = total_num_groups))
names(df_names) <- c("cl", "network")

#construct mean_sd_sem data frame
df_mean_sd_sem <- NULL
for(network in networks) {
  mean_sd_sem <- data_frame_mean_sd_sem(data_frame = subset_with_clusters_AG_matched, variable = network, hydra_cluster = num_clusters)
  df_mean_sd_sem <- rbind(df_mean_sd_sem, mean_sd_sem)
}

#combine data frames and remove the extra cluster names
all_mean_sd_sem <- data.frame(df_names, df_mean_sd_sem)
all_mean_sd_sem <- subset(all_mean_sd_sem, select = -c(cl.1))
                          
for(network in networks){
  for(num in 1:total_num_groups) {
    clst <- groups[num,1]
    meas <- groups[num,2]
    mean_for_eval <- paste("mean(subset_with_clusters_AG_matched$", network, "[which(subset_with_clusters_AG_matched$Hydra_k3 == ", groups[num,2], ")])", sep="")
    mean_grp <- eval(parse(text=as.name(mean_for_eval)))
    all_mean_sd_sem$mean[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$network == network)] <- mean_grp
    
    sd_for_eval <- paste("sd(subset_with_clusters_AG_matched$", network, "[which(subset_with_clusters_AG_matched$Hydra_k3 == ", groups[num,2], ")])", sep="")
    sd_grp <- eval(parse(text=as.name(sd_for_eval)))
    all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$network == network)] <- sd_grp
  #  all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$network == network)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$network == network)]/sqrt(nrow(subset_with_clusters_AG_matched))
    
    #THIS WAS CHANGED 8/8, sem should be based on the number of subjects in each group!
    all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$network == network)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$network == network)]/sqrt(length(which(subset_with_clusters_AG_matched$Hydra_k3 == meas)))
  }
}


#add sems to networks_for_plot
#networks_for_plot$sem <- all_sem_one_col
#names(networks_for_plot) <- c("cluster", "network", "z_score", "sem")
ggplot(data = all_mean_sd_sem, aes(x = network, y = mean, group = cl)) +  ylab("Community Connectivity") +
  geom_line(aes(color=cl)) +
  geom_point(aes(color=cl)) + 
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.1) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  ggtitle("Hydra cluster by Network Connectivity")

####################
###within only
####################
#construct data frame of names of connectivity groups
df_names_within <- data.frame(rep(groups$cl, num_within), rep(within, each = total_num_groups))
names(df_names_within) <- c("cl", "network")

#construct mean_sd_sem data frame
df_mean_sd_sem_within <- NULL
for(network in within) {
  mean_sd_sem <- data_frame_mean_sd_sem(data_frame = subset_with_clusters_AG_matched, variable = network, hydra_cluster = num_clusters)
  df_mean_sd_sem_within <- rbind(df_mean_sd_sem_within, mean_sd_sem)
}

#combine data frames and remove the extra cluster names
all_mean_sd_sem_within <- data.frame(df_names_within, df_mean_sd_sem_within)
all_mean_sd_sem_within <- subset(all_mean_sd_sem_within, select = -c(cl.1))
                          
for(network in within){
  for(num in 1:total_num_groups) {
    clst <- groups[num,1]
    meas <- groups[num,2]
    mean_for_eval <- paste("mean(subset_with_clusters_AG_matched$", network, "[which(subset_with_clusters_AG_matched$Hydra_k3 == ", groups[num,2], ")])", sep="")
    mean_grp <- eval(parse(text=as.name(mean_for_eval)))
    all_mean_sd_sem_within$mean[which(all_mean_sd_sem_within$cl == clst & all_mean_sd_sem_within$network == network)] <- mean_grp
    
    sd_for_eval <- paste("sd(subset_with_clusters_AG_matched$", network, "[which(subset_with_clusters_AG_matched$Hydra_k3 == ", groups[num,2], ")])", sep="")
    sd_grp <- eval(parse(text=as.name(sd_for_eval)))
    all_mean_sd_sem_within$sd[which(all_mean_sd_sem_within$cl == clst & all_mean_sd_sem_within$network == network)] <- sd_grp
  #  all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$network == network)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$network == network)]/sqrt(nrow(subset_with_clusters_AG_matched))
    
    #THIS WAS CHANGED 8/8, sem should be based on the number of subjects in each group!
    all_mean_sd_sem_within$sem[which(all_mean_sd_sem_within$cl == clst & all_mean_sd_sem_within$network == network)] <- all_mean_sd_sem_within$sd[which(all_mean_sd_sem_within$cl == clst & all_mean_sd_sem_within$network == network)]/sqrt(length(which(subset_with_clusters_AG_matched$Hydra_k3 == meas)))
  }
}


#add sems to networks_for_plot
#networks_for_plot$sem <- all_sem_one_col
#names(networks_for_plot) <- c("cluster", "network", "z_score", "sem")
ggplot(data = all_mean_sd_sem_within, aes(x = network, y = mean, group = cl)) +  ylab("Community Connectivity") +
  geom_line(aes(color=cl)) +
  geom_point(aes(color=cl)) + 
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.1) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  ggtitle("Hydra cluster by WITHIN Network Connectivity")

###################
###between only
###################
#construct data frame of names of connectivity groups
df_names_between <- data.frame(rep(groups$cl, num_between), rep(between, each = total_num_groups))
names(df_names_between) <- c("cl", "network")

#construct mean_sd_sem data frame
df_mean_sd_sem_between <- NULL
for(network in between) {
  mean_sd_sem <- data_frame_mean_sd_sem(data_frame = subset_with_clusters_AG_matched, variable = network, hydra_cluster = num_clusters)
  df_mean_sd_sem_between <- rbind(df_mean_sd_sem_between, mean_sd_sem)
}

#combine data frames and remove the extra cluster names
all_mean_sd_sem_between <- data.frame(df_names_between, df_mean_sd_sem_between)
all_mean_sd_sem_between <- subset(all_mean_sd_sem_between, select = -c(cl.1))
                          
for(network in between){
  for(num in 1:total_num_groups) {
    clst <- groups[num,1]
    meas <- groups[num,2]
    mean_for_eval <- paste("mean(subset_with_clusters_AG_matched$", network, "[which(subset_with_clusters_AG_matched$Hydra_k3 == ", groups[num,2], ")])", sep="")
    mean_grp <- eval(parse(text=as.name(mean_for_eval)))
    all_mean_sd_sem_between$mean[which(all_mean_sd_sem_between$cl == clst & all_mean_sd_sem_between$network == network)] <- mean_grp
    
    sd_for_eval <- paste("sd(subset_with_clusters_AG_matched$", network, "[which(subset_with_clusters_AG_matched$Hydra_k3 == ", groups[num,2], ")])", sep="")
    sd_grp <- eval(parse(text=as.name(sd_for_eval)))
    all_mean_sd_sem_between$sd[which(all_mean_sd_sem_between$cl == clst & all_mean_sd_sem_between$network == network)] <- sd_grp
  #  all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$network == network)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$network == network)]/sqrt(nrow(subset_with_clusters_AG_matched))
    
    #THIS WAS CHANGED 8/8, sem should be based on the number of subjects in each group!
    all_mean_sd_sem_between$sem[which(all_mean_sd_sem_between$cl == clst & all_mean_sd_sem_between$network == network)] <- all_mean_sd_sem_between$sd[which(all_mean_sd_sem_between$cl == clst & all_mean_sd_sem_between$network == network)]/sqrt(length(which(subset_with_clusters_AG_matched$Hydra_k3 == meas)))
  }
}


#add sems to networks_for_plot
#networks_for_plot$sem <- all_sem_one_col
#names(networks_for_plot) <- c("cluster", "network", "z_score", "sem")
ggplot(data = all_mean_sd_sem_between, aes(x = network, y = mean, group = cl)) +  ylab("Community Connectivity") +
  geom_line(aes(color=cl)) +
  geom_point(aes(color=cl)) + 
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.1) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  ggtitle("Hydra cluster by BETWEEN Network Connectivity")

#bar graph
ggplot(all_mean_sd_sem_between, aes(x = cl, y = mean, fill = cl)) + geom_col() + 
    geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem),width=.2,position=position_dodge(.9)) + 
    xlab("Clusters") + ylab(paste0("Connectivity")) + 
    ggtitle(paste0("Connectivity between Task active/DMN by Cluster"))  #scale_fill_discrete(breaks=cl) +
    #guides(fill=guide_legend(title=NULL)) 
  
```


FDR correction 
```{r FDR Correction, echo = FALSE, fig.width=10}

###################################################
## Extracting anovas with significant p values ####
###################################################

#lm agesq
#Looking at Hydra_k3
#Look at model summaries
models_anova_lm_agesq <- lapply(network_cluster_stats_anova_lm_agesq_AG_matched, summary)

#Pull p-values
p_anova_lm_agesq <- sapply(network_cluster_stats_anova_lm_agesq_AG_matched, function(v) v$"Pr(>F)"[1]) #$coef[,"Pr(>F)"][2]) #get the p value for dep binarized

#Convert to data frame
p_anova_lm_agesq <- as.data.frame(p_anova_lm_agesq)

#print BEFORE FDR correction 
print("LM Agesq anova scores, BEFORE FDR correction: i.e., uncorrected")
print(p_anova_lm_agesq)

#Print original p-values to three decimal places
p_round_anova_lm_agesq <- round(p_anova_lm_agesq,3)

#FDR correct p-values
pfdr_anova_lm_agesq <- p.adjust(p_anova_lm_agesq[,1],method="fdr")

#Convert to data frame
pfdr_anova_lm_agesq <- as.data.frame(pfdr_anova_lm_agesq)
row.names(pfdr_anova_lm_agesq) <- networks

#To print fdr-corrected p-values to three decimal places
pfdr_round_anova_lm_agesq <- round(pfdr_anova_lm_agesq,3)

#List the components that survive FDR correction
network_fdr_anova_lm_agesq <- row.names(pfdr_anova_lm_agesq)[pfdr_anova_lm_agesq<0.05]

#make a data frame with names and fdr values (rounded to 3 decimals)
network_names_and_fdr_values_anova_lm_agesq <- data.frame(cbind(network_fdr_anova_lm_agesq, round(pfdr_anova_lm_agesq[pfdr_anova_lm_agesq<0.05],3)))

#add titles to names_and_fdr tables
names(network_names_and_fdr_values_anova_lm_agesq) <- c("network", "p_FDR_corr")

print("LM Agesq- Mean centered age that was then squared, FDR corrected")
print(network_names_and_fdr_values_anova_lm_agesq)

#####separating within and between connectivity

within_lm <- network_cluster_stats_lm_agesq_AG_matched[within]
between_lm <- network_cluster_stats_lm_agesq_AG_matched[!is.element(network_cluster_stats_anova_lm_agesq_AG_matched, within_lm)]

within_anova <- network_cluster_stats_anova_lm_agesq_AG_matched[within]
between_anova<- network_cluster_stats_anova_lm_agesq_AG_matched[!is.element(network_cluster_stats_anova_lm_agesq_AG_matched, within_anova)]

within_fdr <- fdr_anova(data_frame = within_anova)
between_fdr <- fdr_anova(data_frame = between_anova)

print("FDR corrected- within communities")
print(within_fdr)

print("FDR corrected - between communities")
print(between_fdr)

print("Pairwise contrasts, within communities, fdr_corrected")
pair_output_within <- pairwise_contrasts_3clusters(within_lm, within_fdr)
print(pair_output_within) #call 
#print(pairwise_contrasts_within_Hydra_k3)

print("Pairwise contrasts, between communities, fdr_corrected")
pair_output_between <- pairwise_contrasts_3clusters(between_lm, between_fdr)
print(pair_output_between) #call 

#print(pairwise_contrasts_between_Hydra_k3)


######################################################
####Pairwise t-tests for anova-corrected lm means ####
######################################################
#######THIS ONLY WORKS FOR 3 CLUSTERS

#put lm model into emmeans format
network_emmodel_lm_agesq_AG_matched <- lapply(network_cluster_stats_lm_agesq_AG_matched, function(x) {as.list(ref_grid(x))})
network_emmgrid_lm_agesq_AG_matched <- lapply(network_emmodel_lm_agesq_AG_matched, function(x) {as.emmGrid(x)})

#run emmeans
network_emmeans_lm_agesq_AG_matched <- lapply(network_emmgrid_lm_agesq_AG_matched, function(x) {emmeans(x, "Hydra_k3")})

#run pairwise contrasts
network_emmpairs_lm_agesq_AG_matched <- lapply(network_emmeans_lm_agesq_AG_matched, function(x) {pairs(x)})

#Only include stuff that was fdr corrected (i.e., only keep parts of the model (or only display) ones that are corrected),this will be null if nothing was corrected
network_emmpairs_lm_agesq_AG_matched_FDR_corrected <- network_emmpairs_lm_agesq_AG_matched[c(network_fdr_anova_lm_agesq)]


################
  ####Corrected #######
######Make table of contrasts, rows are names of brain regions that are fdr corrected, columns are contrasts, values are pvalues

#contrast names, -1 = controls, 1-3 are clusters
contrast_names <- c("-1 - 1", "-1 - 2", "-1 - 3", "1 - 2", "1 - 3", "2 - 3")
#go through each fdr corrected brain region, and extract p values
contrast_table <- lapply(network_emmpairs_lm_agesq_AG_matched_FDR_corrected, function(x) {round(summary(x)$p.value,3)})
#get the names of the brain regions that were fdr corrected
fdr_corrected_brain_regions <- names(contrast_table)
#build table that will hold the name of the brain region and the p values
pairwise_table <- data.frame(matrix(nrow = length(fdr_corrected_brain_regions), ncol = 6))
#give the appropriate names
rownames(pairwise_table) <- fdr_corrected_brain_regions
colnames(pairwise_table) <- contrast_names

#loop through each brain region, and manually assign the columns to be the p values
for (region in fdr_corrected_brain_regions)
{
  pair_pval <- contrast_table[[region]]
  pairwise_table[region,] <- pair_pval
}

#get the mprage out of the name

#Add FDR correction
pairwise_table_with_fdr <- pairwise_table
pairwise_table_with_fdr$p_FDR_corr <- network_names_and_fdr_values_anova_lm_agesq$p_FDR_corr

#print values
print("LM Agesq pairwise contrasts for FDR corrected values Cortical network")
print(pairwise_table)

print ("LM Agesq pairwise contrasts and FDR corr Cortical network")
print(pairwise_table_with_fdr)

sapply(network_emmpairs_lm_agesq_AG_matched_FDR_corrected, function(x) {print(x)})

######------------------------
  ####Uncorrected######
######Make table of contrasts, rows are names of brain regions that are fdr corrected, columns are contrasts, values are pvalues

#contrast names, -1 = controls, 1-3 are clusters
contrast_names <- c("-1 - 1", "-1 - 2", "-1 - 3", "1 - 2", "1 - 3", "2 - 3")
#go through each fdr corrected brain region, and extract p values
contrast_table <- lapply(network_emmpairs_lm_agesq_AG_matched, function(x) {round(summary(x)$p.value,3)})
#get the names of the brain regions that were fdr corrected
brain_regions <- names(contrast_table)
#build table that will hold the name of the brain region and the p values
pairwise_table <- data.frame(matrix(nrow = length(brain_regions), ncol = 6))
#give the appropriate names
rownames(pairwise_table) <- brain_regions
colnames(pairwise_table) <- contrast_names

#loop through each brain region, and manually assign the columns to be the p values
for (region in brain_regions)
{
  pair_pval <- contrast_table[[region]]
  pairwise_table[region,] <- pair_pval
}

#Add FDR correction
#pairwise_table_with_fdr <- pairwise_table
#pairwise_table_with_fdr$p_FDR_corr <- network_names_and_fdr_values_anova_lm_agesq$p_FDR_corr

#print values
print("LM Agesq pairwise contrasts UNCORRECTED values Cortical network ")
print(pairwise_table)


sapply(network_emmpairs_lm_agesq_AG_matched, function(x) {print(x)})



#####------------------------

#########################################################
#checkmodel with visreg, uncomment when want to check####
#########################################################
#invisible(lapply(network_cluster_stats_lm_AG_matched, function(x) {visreg(x)}))

```



