---
title: "Nback Activation, matched age and sex, n304, Hydra K3, r400, 7 communities, NEW HYDRA"
author: "Erica Baller"
date: "10/26/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 9)
library(visreg)
library(mgcv)
library(tableone)
library(dplyr)
library(plm)
library(MatchIt)
library(tidyr)
library(ggplot2)
library(reshape)
library(emmeans)
library(MASS)
theme_update(plot.title = element_text(hjust = 0.5))
source("~/BBL/from_chead/ballerDepHeterogen/ballerDepHeterogenScripts/Hydra_functions.R")

```

## R Markdown

This script goes through demographics, Schaefer scores, health, and psych summaries, adds clustering information, runs statistics and makes graphs from results.

Part 1 : Read in csv.s
  -This script reads in demographics, Nbackfactor scores from jneurosci paper, health and psych summaries, merges them, removes NAs, codes and separates by depression.

Part 2 : merge with hydra
  -It then merges these documents with hydra output (made in cbica), adding Hydra_k1 through Hydra_k10 columns (which represent the number of clusters)
  -The script reads in 3 different types of groups (matched)

Part 3 : Demographics tables
  - Demographics tables matched
  
Part 4 : Graphing
  - Graphs were then made.  
    *For continuous variables(age, medu1), the graphs represent means, with SEM as error bars
    *For categorical variables (race, sex) the graphs are percentages (caucasian, male) per group, with chisq used to calculate significance

Part 5 : LM/GAM/LM with Agesq
  -The script then runs LM on each schaefer parcel (parcel ~ hydra_group + age + sex). 
   - Does gam (parcel ~ hydra_group + s(age) + sex + averageManualRating)
   - Does LM with ageSq (parcel ~ hydra_group + ageSq + sex + averageManualRating)
  -There is a test option that does this for all Schaefer measures and all hydra groups, but for the remainder of the analysis, Hydra_k3 was the only classification more deeply explored.

Part 6 : Anovas
  -Anovas were also run on the results of the LM of each parcel value by cluster.


Part 7 : FDR Correction
  -FDR correction was calculated for each parcel measure ANOVA output
  -A table of the results was extracted
  


```{r jneurosci, echo = FALSE}
#######################################################
############ READ IN, MERGE AND SUBSET DATA############
#######################################################
num_clusters <- 3
resolution <- 400
num_communities <- 7

#get the cluster titles i.e TD, cluster 1, cluster 2, cluster 3
cluster_titles <- get_cluster_titles(hydra_cluster = num_clusters)

#get names of communities- ie default, frontoparietal, ventral salience
community_names_list <- get_community_names(num_communities) #returns the community names, within and between names arrays

#parcellations for use later in lm, in this case it is the community networks
parcellations <- community_names_list[[1]]

#read in csvs
dem_and_cluster_data <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/results/csvs/subset_with_T1_NbackFC_and_dem_with_clusters_NEW_HYDRA.csv", header = TRUE, sep = " ")

filename <- Sys.glob(paste0("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/neuroimaging/processed_data/nback_schaefer_means/n1601_r", resolution, "_com", num_communities, "_means.csv"))

nback_by_community_data <- read.table(file=filename, sep = "") #1193 of 1601 are complete data sets 

#remove people with NA in their communities

nback_by_community_data <- nback_by_community_data[which(!is.na(rowSums(nback_by_community_data))),]

#Get cluster and network names
clusters <- names(dem_and_cluster_data[grep ("Hydra", names(dem_and_cluster_data))])

#make vector to rename nback communities from 1-7 or 1-17 to actually have the names of the networks
new_titles_of_nback_community_info <- c("bblid", "scanid", community_names_list[[1]])

#rename nback_by_community_data titles
names(nback_by_community_data) <- new_titles_of_nback_community_info

#get number of measures (to be used later on when trying to make graphs), for every different modality WILL HAVE TO CHANGE THIS
num_measures <- num_communities

#Coerce values into factor format
hydra_names <- clusters

dem_and_cluster_data[hydra_names] <- lapply(dem_and_cluster_data[clusters], factor)
dem_and_cluster_data$sex <- as.factor(dem_and_cluster_data$sex)
dem_and_cluster_data$race <- as.factor(dem_and_cluster_data$race)

#merge
subset_with_clusters_AG_matched <- merge(nback_by_community_data, dem_and_cluster_data, by = "bblid") #from 368 -> 351 after removing people with NAs

#subset_with_clusters_AG_matched <- subset_with_clusters_AG_matched[!is.na(subset_with_clusters_AG_matched$limbic),]
#sum all columns and make new variable.  Use which to get the indexes of the variables to keep, and then subset subset_with_clusters_AG_matched to keep only those. 
```

##Demographics Table

```{r Demographics, echo = FALSE}
#############################
####### Demographics ########
#############################
make_demographics_table(data_frame = subset_with_clusters_AG_matched, hydra_cluster = num_clusters)


```

#graphs of demographics
```{r Graphs by cluster, echo=FALSE}

#######Chi-square for males/females and race########
##########By males, and by caucasians ##############


#Chi squared 
chisq_matched_sex <- chi_sq(data_frame = subset_with_clusters_AG_matched, "sex", num_clusters)
chisq_matched_race <- chi_sq(data_frame = subset_with_clusters_AG_matched, "race_binarized", num_clusters)

#get means/stds
total_people_Hydra <- total_people_per_cluster(data_frame = subset_with_clusters_AG_matched, hydra_cluster = num_clusters)

num_men_all_clusters <- total_people_per_cluster_by_group(data_frame = subset_with_clusters_AG_matched, variable = "sex", hydra_cluster = num_clusters, group_val = 1)
num_caucasian_all_clusters <- total_people_per_cluster_by_group(data_frame = subset_with_clusters_AG_matched, variable = "race_binarized", hydra_cluster = num_clusters, group_val = 1)

percent_men_all_clusters <- (num_men_all_clusters/total_people_Hydra) * 100
percent_caucasian_all_clusters <- (num_caucasian_all_clusters/total_people_Hydra)*100

p_values <- c("", chisq_matched_sex$p.value, "", chisq_matched_race$p.value)

dat_sex_race <- data.frame(cl = c(cluster_titles, "Significance"), 
                           num_males = c(num_men_all_clusters, "---"),
                           percent_males = round(c(percent_men_all_clusters, chisq_matched_sex$p.value), 2), 
                           num_caucasians = c(num_caucasian_all_clusters, "---"),
                           percent_caucasian = round(c(percent_caucasian_all_clusters, chisq_matched_race$p.value),2))
dat_sex_race_no_significance <-  data.frame(cl = cluster_titles, 
                                            num_males = (num_men_all_clusters),
                                            percent_males = percent_men_all_clusters, 
                                            num_caucasians = num_caucasian_all_clusters,
                                            percent_caucasian = percent_caucasian_all_clusters)                 
percentages <- data.frame(cl=cluster_titles, percent_males = percent_men_all_clusters, percent_caucasians = percent_caucasian_all_clusters)
percentages_for_plot <- melt(percentages, id.vars = "cl")
names(percentages_for_plot) <- c("cluster", "group", "percent")

#Set Titles for plots
title1 <- paste0("Hydra_k", num_clusters, " Percentages")

if(chisq_matched_sex$p.value < 0.05) {
  title2 <- paste0("Hydra_k", num_clusters, "% Male, p < 0.05")
} else {
  title2 <- paste0("Hydra_k", num_clusters, "% Male, p = ", round(chisq_matched_sex$p.value, 2))
}

if(chisq_matched_race$p.value < 0.05) {
  title3 <- paste0("Hydra_k", num_clusters, "% Caucasian, p < 0.05")
} else {
  title3 <- paste0("Hydra_k", num_clusters, "% Caucasian, p = ", round(chisq_matched_race$p.value, 2))
}

#plot
ggplot(data = percentages_for_plot, aes(x = group, y = percent, group = cluster)) + 
  geom_line(aes(color=cluster)) +
  geom_point(aes(color=cluster)) + 
  ggtitle(title1)

ggplot(dat_sex_race_no_significance, aes(x = cl, y = percent_males, fill=cl)) + geom_col() +
  scale_x_discrete(limits=cluster_titles) + ylim(0, 100) + xlab("Clusters") + ylab("% Male") + 
  ggtitle(title2) + scale_fill_discrete(breaks=cluster_titles) +
  guides(fill=guide_legend(title=NULL))

ggplot(dat_sex_race_no_significance, aes(x = cl, y = percent_caucasian, fill=cl)) + geom_col() + 
  scale_x_discrete(limits=cluster_titles) + ylim(0, 100) + xlab("Clusters") + ylab("% Caucasian") + 
  ggtitle(title3) + scale_fill_discrete(breaks=cluster_titles) + 
  guides(fill=guide_legend(title=NULL))

#############################
######### Bar Graphs ########
#############################

variable_name_string <- c("age", "medu") #this allows you to specify the actual titles, if different from the data frame titles
plot_list <- plot_continuous_variables(data_frame = subset_with_clusters_AG_matched, var1 = "age_in_years", var2 = "medu1", hydra_cluster = num_clusters, optional_variable_name_string = variable_name_string)
for(x in 1:length(plot_list)){
  print(plot_list[[x]])
}

```

#Stats
```{r stats, echo = FALSE}
#################################
# Linear Model for each measure #
##### Results stored in list ####
#################################



#### All Hydra clusters in embedded lis t######
#parcellation_cluster_stats_lm_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
#{
 # parcellation_cluster_stats_lm_AG_matched_withincluster<- lapply(parcellations, cluster=as.name(cluster), function(parcellation, cluster) 
#  {
#    parcellation <- as.name(parcellation)
#    lm(substitute(parcellation ~ cluster + sex + age_in_years + nbackRelMeanRMSMotion, list(parcellation = parcellation, cluster = cluster)), data = #subset_with_clusters_AG_matched)
#  })
#  setNames(parcellation_cluster_stats_lm_AG_matched_withincluster, parcellations)
#})

#names(parcellation_cluster_stats_lm_AG_matched_by_cluster_1through10) <- clusters


#gam
#parcellation_cluster_stats_gam_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
#{
 #parcellation_cluster_stats_gam_AG_matched_withincluster<- lapply(parcellations, cluster=as.name(cluster), function(parcellation, cluster) 
 #{
  #  parcellation <- as.name(parcellation)
   # gam(substitute(parcellation ~ cluster + sex + s(age_in_years) + nbackRelMeanRMSMotion, list(parcellation = parcellation, cluster = cluster)), #data = subset_with_clusters_AG_matched)
#  })
 #setNames(parcellation_cluster_stats_gam_AG_matched_withincluster, parcellations)
#})
#names(parcellation_cluster_stats_gam_AG_matched_by_cluster_1through10) <- clusters

#LM with mean-centered, squared age- quadratic term#

#parcellation_cluster_stats_lm_agesq_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
#{
 # parcellation_cluster_stats_lm_agesq_AG_matched_withincluster<- lapply(parcellations, cluster=as.name(cluster), function(parcellation, cluster) 
#  {
 #   parcellation <- as.name(parcellation)
  #  lm(substitute(parcellation ~ cluster + sex + age_in_years + ageSq + nbackRelMeanRMSMotion, list(parcellation = parcellation, cluster = cluster)), data = subset_with_clusters_AG_matched)
  #})
  #setNames(parcellation_cluster_stats_lm_agesq_AG_matched_withincluster, parcellations)
#})
#names(parcellation_cluster_stats_lm_agesq_AG_matched_by_cluster_1through10) <- clusters


##### Just Hydra_3 clusters ######
#lm
parcellation_cluster_stats_lm_AG_matched <- lapply(parcellations, function(parcellation) 
{
  lm(substitute(i ~ Hydra_k3 + sex + age_in_years + nbackRelMeanRMSMotion, list(i = as.name(parcellation))), data = subset_with_clusters_AG_matched)
})
names(parcellation_cluster_stats_lm_AG_matched) <- parcellations

#gam
parcellation_cluster_stats_gam_AG_matched <- lapply(parcellations, function(parcellation) 
{
  parcellation = as.name(parcellation)
  gam(substitute(parcellation ~ Hydra_k3 + sex + s(age_in_years) + nbackRelMeanRMSMotion, list(parcellation = parcellation)), data = subset_with_clusters_AG_matched, method="REML")
})
names(parcellation_cluster_stats_gam_AG_matched) <- parcellations

#lm ageSq and mean centered
parcellation_cluster_stats_lm_agesq_AG_matched <- lapply(parcellations, function(parcellation) 
{
  lm(substitute(i ~ Hydra_k3 + sex + age_in_years + ageSq + nbackRelMeanRMSMotion, list(i = as.name(parcellation))), data = subset_with_clusters_AG_matched)
})
names(parcellation_cluster_stats_lm_agesq_AG_matched) <- parcellations



##############################
####### Statistics ###########
##############################

######## All hydra clusters, Anova results ########

#lm
#parcellation_cluster_stats_anova_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
#{
 # parcellation_cluster_stats_anova_AG_withincluster <- lapply(parcellations, cluster=as.name(cluster), function(parcellation, cluster) 
#  {
 #    parcellation <- as.name(parcellation)
  #   anova(lm(substitute(parcellation ~ cluster + sex + age_in_years + nbackRelMeanRMSMotion, list(parcellation = parcellation, cluster = cluster)), data = subset_with_clusters_AG_matched))
  #})
  #setNames(parcellation_cluster_stats_anova_AG_withincluster, parcellations)
#})
#names(parcellation_cluster_stats_anova_AG_matched_by_cluster_1through10) <- clusters

#gam anova all clusters
#parcellation_cluster_stats_anova_gam_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
#{
 # parcellation_cluster_stats_anova_gam_AG_withincluster <- lapply(parcellations, cluster=as.name(cluster), function(parcellation, cluster) 
  #{
   #  parcellation <- as.name(parcellation)
    # anova(gam(substitute(parcellation ~ cluster + sex + s(age_in_years) + nbackRelMeanRMSMotion, list(parcellation = parcellation, cluster = cluster)), data = subset_with_clusters_AG_matched))
  #})
  #setNames(parcellation_cluster_stats_anova_gam_AG_withincluster, parcellations)
#})
#names(parcellation_cluster_stats_anova_gam_AG_matched_by_cluster_1through10) <- clusters

#lm agesq anova all clusters
#parcellation_cluster_stats_anova_lm_agesq_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
#{
 # parcellation_cluster_stats_anova_lm_agesq_AG_withincluster <- lapply(parcellations, cluster=as.name(cluster), function(parcellation, cluster) 
#  {
 #    parcellation <- as.name(parcellation)
  #   anova(lm(substitute(parcellation ~ cluster + sex + age_in_years + ageSq + nbackRelMeanRMSMotion, list(parcellation = parcellation, cluster = cluster)), data = subset_with_clusters_AG_matched))
  #})
  #setNames(parcellation_cluster_stats_anova_lm_agesq_AG_withincluster, parcellations)
#})
#names(parcellation_cluster_stats_anova_lm_agesq_AG_matched_by_cluster_1through10) <- clusters


#####Just Hydra 3 clusters ANOVA ########
#lm Hydra K3 Anova
parcellation_cluster_stats_anova_lm_AG_matched <- lapply(parcellation_cluster_stats_lm_AG_matched, anova) 
names(parcellation_cluster_stats_anova_lm_AG_matched) <- parcellations

#gam Hydra K3 ANOVA
parcellation_cluster_stats_anova_gam_AG_matched <- lapply(parcellation_cluster_stats_gam_AG_matched, anova)
names(parcellation_cluster_stats_anova_gam_AG_matched) <- parcellations

#lm Hydra K3 Anova
parcellation_cluster_stats_anova_lm_agesq_AG_matched <- lapply(parcellation_cluster_stats_lm_agesq_AG_matched, anova) 
names(parcellation_cluster_stats_anova_lm_agesq_AG_matched) <- parcellations

#lm Hydra k3 aov
parcellation_cluster_stats_aov_lm_agesq_AG_matched <- lapply(parcellation_cluster_stats_lm_agesq_AG_matched, aov) 
names(parcellation_cluster_stats_aov_lm_agesq_AG_matched) <- parcellations

#tukey
#invisible(parcellation_cluster_stats_tukey_of_aov_lm_agesq_AG_matched <- lapply(parcellation_cluster_stats_aov_lm_agesq_AG_matched, function(y) {TukeyHSD(x = y, which = c("Hydra_k3"), ordered = FALSE, conf.level = 0.95)}))
```

##Results graphically presented
```{r Results graphically presented, echo = FALSE}


#####################################
###### By FC Connectivity Measure ###############
#####################################
#can do with all gender as well, as well as matched/unmatched, etc
#loop through each cluster and each parcellation measure, make text and evaluate the following: mean of each cluster by measure, and sd of each cluster by measure

cluster_titles <- get_cluster_titles(hydra_cluster = num_clusters)
cluster_vector <- get_cluster_numerical_vector(hydra_cluster = num_clusters)
groups <- data.frame(cbind(cluster_titles, cluster_vector))
names(groups) <- c("cl", "numeric")
total_num_groups <- num_clusters + 1

#construct data frame of names of connectivity groups
df_names <- data.frame(rep(groups$cl, num_measures), rep(parcellations, each = total_num_groups))
names(df_names) <- c("cl", "parcellation")

#construct mean_sd_sem data frame
df_mean_sd_sem <- NULL
for(parcellation in parcellations) {
  mean_sd_sem <- data_frame_mean_sd_sem(data_frame = subset_with_clusters_AG_matched, variable = parcellation, hydra_cluster = num_clusters)
  df_mean_sd_sem <- rbind(df_mean_sd_sem, mean_sd_sem)
}

#combine data frames and remove the extra cluster names
all_mean_sd_sem <- data.frame(df_names, df_mean_sd_sem)
all_mean_sd_sem <- subset(all_mean_sd_sem, select = -c(cl.1))
                          
for(parcellation in parcellations){
  for(num in 1:total_num_groups) {
    clst <- groups[num,1]
    meas <- groups[num,2]
    mean_for_eval <- paste("mean(subset_with_clusters_AG_matched$", parcellation, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups[num,2], ")])", sep="")
    mean_grp <- eval(parse(text=as.name(mean_for_eval)))
    all_mean_sd_sem$mean[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$parcellation == parcellation)] <- mean_grp
    
    sd_for_eval <- paste("sd(subset_with_clusters_AG_matched$", parcellation, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups[num,2], ")])", sep="")
    sd_grp <- eval(parse(text=as.name(sd_for_eval)))
    all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$parcellation == parcellation)] <- sd_grp
  #  all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$parcellation == parcellation)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$parcellation == parcellation)]/sqrt(nrow(subset_with_clusters_AG_matched))
    
    #THIS WAS CHANGED 8/8, sem should be based on the number of subjects in each group!
    sem_calc <- paste0("all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$parcellation == parcellation)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$parcellation == parcellation)]/sqrt(length(which(subset_with_clusters_AG_matched$Hydra_k", num_clusters," == meas)))")
    eval(parse(text=as.name(sem_calc)))
  
  }
}


#add sems to parcellations_for_plot
#parcellations_for_plot$sem <- all_sem_one_col
#names(parcellations_for_plot) <- c("cluster", "parcellation", "z_score", "sem")
ggplot(data = all_mean_sd_sem, aes(x = parcellation, y = mean, group = cl)) +  ylab("% signal change") +
  geom_line(aes(color=cl)) +
  geom_point(aes(color=cl)) + 
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   theme(axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 20), title = element_text(size = 20), legend.text = element_text(size = 20)) + 
  ggtitle(paste0("Hydra_k", num_clusters, " by Schaefer resolution ", resolution, ", Community #", num_communities, " Nback"))
```

##FDR correction 
```{r FDR Correction, echo = FALSE, fig.width=10}

###################################################
## Extracting anovas with significant p values ####
###################################################
#lm
#Looking at Hydra_k3, but can redo with nested list
#Look at model summaries
models_anova <- lapply(parcellation_cluster_stats_anova_lm_AG_matched, summary)

#Pull p-values
p_anova <- sapply(parcellation_cluster_stats_anova_lm_AG_matched, function(v) v$"Pr(>F)"[1]) #$coef[,"Pr(>F)"][2]) #get the p value for dep binarized

#Convert to data frame
p_anova <- as.data.frame(p_anova)

#print BEFORE FDR correction 
print("LM anova scores, BEFORE FDR correction, i.e. uncorrected")
print(p_anova)

#Print original p-values to three decimal places
p_round_anova <- round(p_anova,3)

#FDR correct p-values
pfdr_anova <- p.adjust(p_anova[,1],method="fdr")

#Convert to data frame
pfdr_anova <- as.data.frame(pfdr_anova)
row.names(pfdr_anova) <- parcellations

#To print fdr-corrected p-values to three decimal places
pfdr_round_anova <- round(pfdr_anova,3)

#List the NMF components that survive FDR correction
parcellation_fdr_anova <- row.names(pfdr_anova)[pfdr_anova<0.05]

#make a data frame with names and fdr values (rounded to 3 decimals)
parcellation_names_and_fdr_values_anova <- data.frame(cbind(parcellation_fdr_anova, round(pfdr_anova[pfdr_anova<0.05],3)))

#add titles to names_and_fdr tables
names(parcellation_names_and_fdr_values_anova) <- c("parcellation", "p_FDR_corr")

print("LM with FDR values from ANOVA")
print(parcellation_names_and_fdr_values_anova)

#gam

#Looking at Hydra_k3, but can redo with nested list
#Look at model summaries
#models_anova <- lapply(parcellation_cluster_stats_anova_gam_AG_matched, summary)

#Pull p-values
p_anova <- sapply(parcellation_cluster_stats_anova_gam_AG_matched, function(v) v$pTerms.table[1,3])
                    #"Pr(>F)"[1]) #$coef[,"Pr(>F)"][2]) #get the p value for dep binarized

#Convert to data frame
p_anova <- as.data.frame(p_anova)

#print BEFORE FDR correction 
print("GAM anova scores, BEFORE FDR correction, i.e.- uncorrected")
print(p_anova)

#Print original p-values to three decimal places
p_round_anova <- round(p_anova,3)

#FDR correct p-values
pfdr_anova <- p.adjust(p_anova[,1],method="fdr")

#Convert to data frame
pfdr_anova <- as.data.frame(pfdr_anova)
row.names(pfdr_anova) <- parcellations

#To print fdr-corrected p-values to three decimal places
pfdr_round_anova <- round(pfdr_anova,3)

#List things that meet FDR correction
parcellation_fdr_anova <- row.names(pfdr_anova)[pfdr_anova<0.05]

#make a data frame with names and fdr values (rounded to 3 decimals)
parcellation_names_and_fdr_values_anova <- data.frame(cbind(parcellation_fdr_anova, round(pfdr_anova[pfdr_anova<0.05],3)))

#add titles to names_and_fdr tables
names(parcellation_names_and_fdr_values_anova) <- c("parcellation", "p_FDR_corr_GAM")

print("GAM with FDR values from anova")
print(parcellation_names_and_fdr_values_anova)

#lm agesq
#Looking at Hydra_k3
#Look at model summaries
models_anova_lm_agesq <- lapply(parcellation_cluster_stats_anova_lm_agesq_AG_matched, summary)

#Pull p-values
p_anova_lm_agesq <- sapply(parcellation_cluster_stats_anova_lm_agesq_AG_matched, function(v) v$"Pr(>F)"[1]) #$coef[,"Pr(>F)"][2]) #get the p value for dep binarized

#Convert to data frame
p_anova_lm_agesq <- as.data.frame(p_anova_lm_agesq)

#print BEFORE FDR correction 
print("LM Agesq anova scores, BEFORE FDR correction: i.e., uncorrected")
print(p_anova_lm_agesq)

#print("LM agesq anova scores, BEFORE FDR correction, p <0.05")
#anova_before_correction_p05 <- as.data.frame(p_anova_lm_agesq[p_anova_lm_agesq <0.05])
#row.names(anova_before_correction_p05) <- row.names(anova_before_correction_p05)[p_round_anova_lm_agesq<0.05]


#Print original p-values to three decimal places
p_round_anova_lm_agesq <- round(p_anova_lm_agesq,3)

#FDR correct p-values
pfdr_anova_lm_agesq <- p.adjust(p_anova_lm_agesq[,1],method="fdr")

#Convert to data frame
pfdr_anova_lm_agesq <- as.data.frame(pfdr_anova_lm_agesq)
row.names(pfdr_anova_lm_agesq) <- parcellations

#To print fdr-corrected p-values to three decimal places
pfdr_round_anova_lm_agesq <- round(pfdr_anova_lm_agesq,3)

#List the components that survive FDR correction
parcellation_fdr_anova_lm_agesq <- row.names(pfdr_anova_lm_agesq)[pfdr_anova_lm_agesq<0.05]

#make a data frame with names and fdr values (rounded to 3 decimals)
parcellation_names_and_fdr_values_anova_lm_agesq <- data.frame(cbind(parcellation_fdr_anova_lm_agesq, round(pfdr_anova_lm_agesq[pfdr_anova_lm_agesq<0.05],3)))

#add titles to names_and_fdr tables
names(parcellation_names_and_fdr_values_anova_lm_agesq) <- c("parcellation", "p_FDR_corr")

print("LM Agesq- Mean centered age that was then squared, FDR corrected")
print(parcellation_names_and_fdr_values_anova_lm_agesq)

######################################################
####Pairwise t-tests for anova-corrected lm means ####
######################################################
#######THIS ONLY WORKS FOR 3 CLUSTERS

#put lm model into emmeans format
parcellation_emmodel_lm_agesq_AG_matched <- lapply(parcellation_cluster_stats_lm_agesq_AG_matched, function(x) {as.list(ref_grid(x))})
parcellation_emmgrid_lm_agesq_AG_matched <- lapply(parcellation_emmodel_lm_agesq_AG_matched, function(x) {as.emmGrid(x)})

#run emmeans
parcellation_emmeans_lm_agesq_AG_matched <- lapply(parcellation_emmgrid_lm_agesq_AG_matched, function(x) {emmeans(x, "Hydra_k3")})

#run pairwise contrasts
parcellation_emmpairs_lm_agesq_AG_matched <- lapply(parcellation_emmeans_lm_agesq_AG_matched, function(x) {pairs(x)})

#Only include stuff that was fdr corrected (i.e., only keep parts of the model (or only display) ones that are corrected),this will be null if nothing was corrected
parcellation_emmpairs_lm_agesq_AG_matched_FDR_corrected <- parcellation_emmpairs_lm_agesq_AG_matched[c(parcellation_fdr_anova_lm_agesq)]


################
  ####Corrected #######
######Make table of contrasts, rows are names of brain regions that are fdr corrected, columns are contrasts, values are pvalues

#contrast names, -1 = controls, 1-3 are clusters
contrast_names <- c("-1 - 1", "-1 - 2", "-1 - 3", "1 - 2", "1 - 3", "2 - 3")
#contrast_names <- c("-1 - 1", "-1 - 2", "1 2")

#go through each fdr corrected brain region, and extract p values
contrast_table <- lapply(parcellation_emmpairs_lm_agesq_AG_matched_FDR_corrected, function(x) {round(summary(x)$p.value,3)})
#get the names of the brain regions that were fdr corrected
fdr_corrected_brain_regions <- names(contrast_table)

#build table that will hold the name of the brain region and the p values
pairwise_table <- data.frame(matrix(nrow = length(fdr_corrected_brain_regions), ncol = 6))
#pairwise_table <- data.frame(matrix(nrow = length(fdr_corrected_brain_regions), ncol = 3))

#give the appropriate names
rownames(pairwise_table) <- fdr_corrected_brain_regions
colnames(pairwise_table) <- contrast_names

#loop through each brain region, and manually assign the columns to be the p values
for (region in fdr_corrected_brain_regions)
{
  pair_pval <- contrast_table[[region]]
  pairwise_table[region,] <- pair_pval
}

#get the mprage out of the name

#Add FDR correction
pairwise_table_with_fdr <- pairwise_table
pairwise_table_with_fdr$p_FDR_corr <- parcellation_names_and_fdr_values_anova_lm_agesq$p_FDR_corr

#print values
#print("LM Agesq pairwise contrasts for FDR corrected values Jneurosci parcellations")
#print(pairwise_table)

print ("LM Agesq pairwise contrasts and FDR corrrected values Jneurosci parcellations")
print(pairwise_table_with_fdr)

sapply(parcellation_emmpairs_lm_agesq_AG_matched_FDR_corrected, function(x) {print(x)})

######------------------------
  ####Uncorrected######  ##### PUT THIS BACK IN IF YOU WANT IT####
######Make table of contrasts, rows are names of brain regions that are fdr corrected, columns are contrasts, values are pvalues

#contrast names, -1 = controls, 1-3 are clusters
contrast_names <- c("-1 - 1", "-1 - 2", "-1 - 3", "1 - 2", "1 - 3", "2 - 3")
####contrast_names <- c("-1 - 1", "-1 - 2", "1 2")

#go through each fdr corrected brain region, and extract p values
#contrast_table <- lapply(parcellation_emmpairs_lm_agesq_AG_matched, function(x) {round(summary(x)$p.value,3)})
#get the names of the brain regions that were fdr corrected
#brain_regions <- names(contrast_table)
#build table that will hold the name of the brain region and the p values
#pairwise_table <- data.frame(matrix(nrow = length(brain_regions), ncol = 6))
#pairwise_table <- data.frame(matrix(nrow = length(brain_regions), ncol = 3))

#give the appropriate names
#rownames(pairwise_table) <- brain_regions
#colnames(pairwise_table) <- contrast_names

#loop through each brain region, and manually assign the columns to be the p values
#for (region in brain_regions)
#{
 # pair_pval <- contrast_table[[region]]
#  pairwise_table[region,] <- pair_pval
#}

#Add FDR correction
##pairwise_table_with_fdr <- pairwise_table
##pairwise_table_with_fdr$p_FDR_corr <- parcellation_names_and_fdr_values_anova_lm_agesq$p_FDR_corr

#print values
#print("LM Agesq pairwise contrasts UNCORRECTED values Jneurosci parcellation ")
#print(pairwise_table)


#sapply(parcellation_emmpairs_lm_agesq_AG_matched, function(x) {print(x)})



#####------------------------

#########################################################
#checkmodel with visreg, uncomment when want to check####
#########################################################
#invisible(lapply(parcellation_cluster_stats_lm_AG_matched, function(x) {visreg(x)}))

```