---
title: "Nback Activation, matched age and sex, n368, Hydra K3, 13 jneurosci labels, generic script"
author: "Erica Baller"
date: "9/4/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 9)
library(visreg)
library(mgcv)
library(tableone)
library(dplyr)
library(plm)
library(MatchIt)
library(tidyr)
library(ggplot2)
library(reshape)
library(emmeans)
library(MASS)
theme_update(plot.title = element_text(hjust = 0.5))
source("~/BBL/from_chead/ballerDepHeterogen/ballerDepHeterogenScripts/Hydra_functions.R")

```

## R Markdown

This script goes through demographics, Schaefer scores, health, and psych summaries, adds clustering information, runs statistics and makes graphs from results.

Part 1 : Read in csv.s
  -This script reads in demographics, Nbackfactor scores from jneurosci paper, health and psych summaries, merges them, removes NAs, codes and separates by depression.

Part 2 : merge with hydra
  -It then merges these documents with hydra output (made in cbica), adding Hydra_k1 through Hydra_k10 columns (which represent the number of clusters)
  -The script reads in 3 different types of groups (matched)

Part 3 : Demographics tables
  - Demographics tables matched
  
Part 4 : Graphing
  - Graphs were then made.  
    *For continuous variables(age, medu1), the graphs represent means, with SEM as error bars
    *For categorical variables (race, sex) the graphs are percentages (caucasian, male) per group, with chisq used to calculate significance

Part 5 : LM/GAM/LM with Agesq
  -The script then runs LM on each schaefer parcel (parcel ~ hydra_group + age + sex). 
   - Does gam (parcel ~ hydra_group + s(age) + sex + averageManualRating)
   - Does LM with ageSq (parcel ~ hydra_group + ageSq + sex + averageManualRating)
  -There is a test option that does this for all Schaefer measures and all hydra groups, but for the remainder of the analysis, Hydra_k3 was the only classification more deeply explored.

Part 6 : Anovas
  -Anovas were also run on the results of the LM of each parcel value by cluster.


Part 7 : FDR Correction
  -FDR correction was calculated for each parcel measure ANOVA output
  -A table of the results was extracted
  


```{r jneurosci, echo = FALSE}


#######################################################
############ READ IN, MERGE AND SUBSET DATA############
#######################################################

num_clusters <- 3
hydra_var <- paste0("Hydra_k", num_clusters)
cluster_titles <- get_cluster_titles(hydra_cluster = num_clusters)

#read in csvs
nback_Factors <- readRDS("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/neuroimaging/nback/nbackFactors_n1601_subjData_20150506.rds")
dem_and_cluster_data <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/results/csvs/subset_with_T1_NbackFC_and_dem_with_clusters.csv", header = TRUE, sep = " ")


#Get cluster and parcellation names
clusters <- names(dem_and_cluster_data[grep ("Hydra", names(dem_and_cluster_data))])
parcellations <- names(nback_Factors[grep ("nback_func_sc", names(nback_Factors))])

#subset nback_Factors because it is so big
nback_Factors_bblid_and_parcellations <- cbind(nback_Factors$bblid, nback_Factors[,parcellations])
colnames(nback_Factors_bblid_and_parcellations)[1] <- "bblid"

#get number of measures (to be used later on when trying to make graphs), for every different modality WILL HAVE TO CHANGE THIS
num_measures <- length(parcellations)

#Coerce values into factor format
hydra_names <- clusters

dem_and_cluster_data[hydra_names] <- lapply(dem_and_cluster_data[clusters], factor)
dem_and_cluster_data$sex <- as.factor(dem_and_cluster_data$sex)
dem_and_cluster_data$race <- as.factor(dem_and_cluster_data$race)

#merge
subset_with_clusters_AG_matched <- merge(nback_Factors_bblid_and_parcellations, dem_and_cluster_data, by = "bblid")



```

##Demographics Table

```{r Demographics, echo = FALSE}
#############################
####### Demographics ########
#############################
make_demographics_table(data_frame = subset_with_clusters_AG_matched, hydra_cluster = num_clusters)


```

#graphs of demographics
```{r Graphs by cluster, echo=FALSE}

#######Chi-square for males/females and race########
##########By males, and by caucasians ##############


#Chi squared 
chisq_matched_sex <- chi_sq(data_frame = subset_with_clusters_AG_matched, "sex", num_clusters)
chisq_matched_race <- chi_sq(data_frame = subset_with_clusters_AG_matched, "race_binarized", num_clusters)

#get means/stds
total_people_Hydra <- total_people_per_cluster(data_frame = subset_with_clusters_AG_matched, hydra_cluster = num_clusters)

num_men_all_clusters <- total_people_per_cluster_by_group(data_frame = subset_with_clusters_AG_matched, variable = "sex", hydra_cluster = num_clusters, group_val = 1)
num_caucasian_all_clusters <- total_people_per_cluster_by_group(data_frame = subset_with_clusters_AG_matched, variable = "race_binarized", hydra_cluster = num_clusters, group_val = 1)

percent_men_all_clusters <- (num_men_all_clusters/total_people_Hydra) * 100
percent_caucasian_all_clusters <- (num_caucasian_all_clusters/total_people_Hydra)*100

p_values <- c("", chisq_matched_sex$p.value, "", chisq_matched_race$p.value)

dat_sex_race <- data.frame(cl = c(cluster_titles, "Significance"), 
                           num_males = c(num_men_all_clusters, "---"),
                           percent_males = round(c(percent_men_all_clusters, chisq_matched_sex$p.value), 2), 
                           num_caucasians = c(num_caucasian_all_clusters, "---"),
                           percent_caucasian = round(c(percent_caucasian_all_clusters, chisq_matched_race$p.value),2))
dat_sex_race_no_significance <-  data.frame(cl = cluster_titles, 
                                            num_males = (num_men_all_clusters),
                                            percent_males = percent_men_all_clusters, 
                                            num_caucasians = num_caucasian_all_clusters,
                                            percent_caucasian = percent_caucasian_all_clusters)                 
percentages <- data.frame(cl=cluster_titles, percent_males = percent_men_all_clusters, percent_caucasians = percent_caucasian_all_clusters)
percentages_for_plot <- melt(percentages, id.vars = "cl")
names(percentages_for_plot) <- c("cluster", "group", "percent")

#Set Titles for plots
title1 <- paste0("Hydra_k", num_clusters, " Percentages")

if(chisq_matched_sex$p.value < 0.05) {
  title2 <- paste0("Hydra_k", num_clusters, "% Male, p < 0.05")
} else {
  title2 <- paste0("Hydra_k", num_clusters, "% Male, p = ", round(chisq_matched_sex$p.value, 2))
}

if(chisq_matched_race$p.value < 0.05) {
  title3 <- paste0("Hydra_k", num_clusters, "% Caucasian, p < 0.05")
} else {
  title3 <- paste0("Hydra_k", num_clusters, "% Caucasian, p = ", round(chisq_matched_race$p.value, 2))
}

#plot
ggplot(data = percentages_for_plot, aes(x = group, y = percent, group = cluster)) + 
  geom_line(aes(color=cluster)) +
  geom_point(aes(color=cluster)) + 
  ggtitle(title1)

ggplot(dat_sex_race_no_significance, aes(x = cl, y = percent_males, fill=cl)) + geom_col() +
  scale_x_discrete(limits=cluster_titles) + ylim(0, 100) + xlab("Clusters") + ylab("% Male") + 
  ggtitle(title2) + scale_fill_discrete(breaks=cluster_titles) +
  guides(fill=guide_legend(title=NULL))

ggplot(dat_sex_race_no_significance, aes(x = cl, y = percent_caucasian, fill=cl)) + geom_col() + 
  scale_x_discrete(limits=cluster_titles) + ylim(0, 100) + xlab("Clusters") + ylab("% Caucasian") + 
  ggtitle(title3) + scale_fill_discrete(breaks=cluster_titles) + 
  guides(fill=guide_legend(title=NULL))

#############################
######### Bar Graphs ########
#############################

variable_name_string <- c("age", "medu") #this allows you to specify the actual titles, if different from the data frame titles
plot_list <- plot_continuous_variables(data_frame = subset_with_clusters_AG_matched, var1 = "age_in_years", var2 = "medu1", hydra_cluster = num_clusters, optional_variable_name_string = variable_name_string)
for(x in 1:length(plot_list)){
  print(plot_list[[x]])
}

```

#Stats
```{r stats, echo = FALSE}
#################################
# Linear Model for each measure #
##### Results stored in list ####
#################################



#### All Hydra clusters in embedded lis t######
#parcellation_cluster_stats_lm_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
#{
 # parcellation_cluster_stats_lm_AG_matched_withincluster<- lapply(parcellations, cluster=as.name(cluster), function(parcellation, cluster) 
#  {
#    parcellation <- as.name(parcellation)
#    lm(substitute(parcellation ~ cluster + sex + age_in_years + nbackRelMeanRMSMotion, list(parcellation = parcellation, cluster = cluster)), data = #subset_with_clusters_AG_matched)
#  })
#  setNames(parcellation_cluster_stats_lm_AG_matched_withincluster, parcellations)
#})

#names(parcellation_cluster_stats_lm_AG_matched_by_cluster_1through10) <- clusters


#gam
#parcellation_cluster_stats_gam_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
#{
 #parcellation_cluster_stats_gam_AG_matched_withincluster<- lapply(parcellations, cluster=as.name(cluster), function(parcellation, cluster) 
 #{
  #  parcellation <- as.name(parcellation)
   # gam(substitute(parcellation ~ cluster + sex + s(age_in_years) + nbackRelMeanRMSMotion, list(parcellation = parcellation, cluster = cluster)), #data = subset_with_clusters_AG_matched)
#  })
 #setNames(parcellation_cluster_stats_gam_AG_matched_withincluster, parcellations)
#})
#names(parcellation_cluster_stats_gam_AG_matched_by_cluster_1through10) <- clusters

#LM with mean-centered, squared age- quadratic term#

#parcellation_cluster_stats_lm_agesq_AG_matched_by_cluster_1through10 <- lapply(clusters, function(cluster)
#{
 # parcellation_cluster_stats_lm_agesq_AG_matched_withincluster<- lapply(parcellations, cluster=as.name(cluster), function(parcellation, cluster) 
#  {
 #   parcellation <- as.name(parcellation)
  #  lm(substitute(parcellation ~ cluster + sex + age_in_years + ageSq + nbackRelMeanRMSMotion, list(parcellation = parcellation, cluster = cluster)), data = subset_with_clusters_AG_matched)
  #})
  #setNames(parcellation_cluster_stats_lm_agesq_AG_matched_withincluster, parcellations)
#})
#names(parcellation_cluster_stats_lm_agesq_AG_matched_by_cluster_1through10) <- clusters


##### Just Hydra_3 clusters ######
#lm
parcellation_cluster_stats_lm_AG_matched <- lapply(parcellations, function(parcellation) 
{
  lm(substitute(parcellation ~ hydra + sex + age_in_years + nbackRelMeanRMSMotion, list(parcellation = as.name(parcellation), hydra = as.name(hydra_var))), data = subset_with_clusters_AG_matched)
})
names(parcellation_cluster_stats_lm_AG_matched) <- parcellations

#gam
parcellation_cluster_stats_gam_AG_matched <- lapply(parcellations, function(parcellation) 
{
  parcellation = as.name(parcellation)
  gam(substitute(parcellation ~ hydra + sex + s(age_in_years) + nbackRelMeanRMSMotion, list(parcellation = parcellation, hydra = as.name(hydra_var))), data = subset_with_clusters_AG_matched, method="REML")
})
names(parcellation_cluster_stats_gam_AG_matched) <- parcellations

#lm ageSq and mean centered
parcellation_cluster_stats_lm_agesq_AG_matched <- lapply(parcellations, function(parcellation) 
{
  lm(substitute(parcellation ~ hydra + sex + age_in_years + ageSq + nbackRelMeanRMSMotion, list(parcellation = as.name(parcellation), hydra = as.name(hydra_var))), data = subset_with_clusters_AG_matched)
})
names(parcellation_cluster_stats_lm_agesq_AG_matched) <- parcellations



##############################
####### Statistics ###########
##############################

######## All hydra clusters, Anova results ########

#####Just Hydra 3 clusters ANOVA ########
#lm Hydra K3 Anova
parcellation_cluster_stats_anova_lm_AG_matched <- lapply(parcellation_cluster_stats_lm_AG_matched, anova) 
names(parcellation_cluster_stats_anova_lm_AG_matched) <- parcellations

#gam Hydra K3 ANOVA
parcellation_cluster_stats_anova_gam_AG_matched <- lapply(parcellation_cluster_stats_gam_AG_matched, anova)
names(parcellation_cluster_stats_anova_gam_AG_matched) <- parcellations

#lm Hydra K3 Anova
parcellation_cluster_stats_anova_lm_agesq_AG_matched <- lapply(parcellation_cluster_stats_lm_agesq_AG_matched, anova) 
names(parcellation_cluster_stats_anova_lm_agesq_AG_matched) <- parcellations

#lm Hydra k3 aov
#parcellation_cluster_stats_aov_lm_agesq_AG_matched <- lapply(parcellation_cluster_stats_lm_agesq_AG_matched, aov) 
#names(parcellation_cluster_stats_aov_lm_agesq_AG_matched) <- parcellations

#tukey
#invisible(parcellation_cluster_stats_tukey_of_aov_lm_agesq_AG_matched <- lapply(parcellation_cluster_stats_aov_lm_agesq_AG_matched, function(y) {TukeyHSD(x = y, which = c("Hydra_k3"), ordered = FALSE, conf.level = 0.95)}))
```

##Results graphically presented
```{r Results graphically presented, echo = FALSE}


#####################################
###### By Nback Parcellation Measure ###############
#####################################
#can do with all gender as well, as well as matched/unmatched, etc
#loop through each cluster and each parcellation measure, make text and evaluate the following: mean of each cluster by measure, and sd of each cluster by measure

cluster_titles <- get_cluster_titles(hydra_cluster = num_clusters)
cluster_vector <- get_cluster_numerical_vector(hydra_cluster = num_clusters)
groups <- data.frame(cbind(cluster_titles, cluster_vector))
names(groups) <- c("cl", "numeric")
total_num_groups <- num_clusters + 1

#construct data frame of names of connectivity groups
df_names <- data.frame(rep(groups$cl, num_measures), rep(parcellations, each = total_num_groups))
names(df_names) <- c("cl", "parcellation")

#construct mean_sd_sem data frame
df_mean_sd_sem <- NULL
for(parcellation in parcellations) {
  mean_sd_sem <- data_frame_mean_sd_sem(data_frame = subset_with_clusters_AG_matched, variable = parcellation, hydra_cluster = num_clusters)
  df_mean_sd_sem <- rbind(df_mean_sd_sem, mean_sd_sem)
}

#combine data frames and remove the extra cluster names
all_mean_sd_sem <- data.frame(df_names, df_mean_sd_sem)
all_mean_sd_sem <- subset(all_mean_sd_sem, select = -c(cl.1))
                          
for(parcellation in parcellations){
  for(num in 1:total_num_groups) {
    clst <- groups[num,1]
    meas <- groups[num,2]
    mean_for_eval <- paste("mean(subset_with_clusters_AG_matched$", parcellation, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups[num,2], ")])", sep="")
    mean_grp <- eval(parse(text=as.name(mean_for_eval)))
    all_mean_sd_sem$mean[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$parcellation == parcellation)] <- mean_grp
    
    sd_for_eval <- paste("sd(subset_with_clusters_AG_matched$", parcellation, "[which(subset_with_clusters_AG_matched$Hydra_k", num_clusters, " == ", groups[num,2], ")])", sep="")
    sd_grp <- eval(parse(text=as.name(sd_for_eval)))
    all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$parcellation == parcellation)] <- sd_grp
  #  all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$parcellation == parcellation)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$parcellation == parcellation)]/sqrt(nrow(subset_with_clusters_AG_matched))
    
    #THIS WAS CHANGED 8/8, sem should be based on the number of subjects in each group!
    sem_calc <- paste0("all_mean_sd_sem$sem[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$parcellation == parcellation)] <- all_mean_sd_sem$sd[which(all_mean_sd_sem$cl == clst & all_mean_sd_sem$parcellation == parcellation)]/sqrt(length(which(subset_with_clusters_AG_matched$Hydra_k", num_clusters," == meas)))")
    eval(parse(text=as.name(sem_calc)))
  
  }
}


#add sems to parcellations_for_plot
#parcellations_for_plot$sem <- all_sem_one_col
#names(parcellations_for_plot) <- c("cluster", "parcellation", "z_score", "sem")
ggplot(data = all_mean_sd_sem, aes(x = parcellation, y = mean, group = cl)) +  ylab("% signal change") +
  geom_line(aes(color=cl)) +
  geom_point(aes(color=cl)) + 
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Hydra cluster by Jneurosci Parcellation in Nback")
```

##FDR correction 
```{r FDR Correction, echo = FALSE, fig.width=10}

fdr_corrected<- fdr_anova(data_frame = parcellation_cluster_stats_anova_lm_agesq_AG_matched)
pairwise_table_with_fdr <- pairwise_contrasts_generic_num_clusters(data_frame_lm = parcellation_cluster_stats_lm_agesq_AG_matched, fdr_anova = fdr_corrected, num_clusters = num_clusters)

print ("LM Agesq pairwise contrasts and FDR corrrected values Jneurosci parcellations")
print(pairwise_table_with_fdr[[4]])
#print(pairwise_table_with_fdr)
#sapply(pairwise_table_with_fdr, function(x) {print(x)})

```