---
title: "CWASMDMR"
author: "Erica Baller"
date: "January 22, 2019"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#source("/data/jux/BBL/projects/ballerDepHeterogen/ballerDepHeterogenScripts/Imaging/cwasmdmr/cwasmdmr_NEW_FROM_AZEEZ_20190109.R")
```

## Uses

This script displays output of CWASMDMR 

#Num subjects: n= 312

#Preprocessing before this script:
Script: combine_rest_nback_idemo_volumes_weighted_n312_20181218.sh
Uses: Concatenated rest, nback and idemo

Script: extract_timeseries_from_concatenated_files_20190118_NOTRANSPOSE.csh
Uses: extracted the timeseries from the concatenated files and output them: row (27) by col (555)
- extracted from 27 functional parcellations from Nback

Script: run_cwasmdmr_from_NEW_AZEEZ_script_made_20190115.R
Inputs: 
 modelfile = '/data/jux/BBL/projects/ballerDepHeterogen/data/neuroimaging/processed_data/concat_restbold_nback_idemo/subject_lists/subj_list_concat_weighted_n312_with_header
s_just_covs_and_Hydra_k3_order_by_scanid.csv'
subjectlist = '/data/jux/BBL/projects/ballerDepHeterogen/data/neuroimaging/processed_data/concat_restbold_nback_idemo/subject_lists/subj_list_n312_concat_rest_nback_idemo_4
mm_27parcels.csv'
Uses: gives an output of P and Z scores
Output: "/data/jux/BBL/projects/ballerDepHeterogen/results/csvs/cwas_output_from_R_script_20190122_pandz.csv" 


## Stats

```{r stats, echo=FALSE}
pandz <- read.csv("/Users/eballer/BBL/from_chead/ballerDepHeterogen/results/csvs/cwas_output_from_R_script_20190122_pandz.csv")
names_of_parcels <- read.table("/Users/eballer/BBL/from_chead/ballerDepHeterogen/data/neuroimaging/nback/parcels/roi27_dictionary.txt", header=FALSE)

#switch order of z and p
names(pandz) <- c("parcel_num", "pval", "z")
zandp <- data.frame(cbind(pandz$parcel_num, pandz$z, pandz$pval))
names_of_parcels<-gsub("nback_func_sc_", "", names_of_parcels$V2)
parcels_plus_stats <- data.frame(cbind(names_of_parcels, zandp))
names(parcels_plus_stats) <- c("brain_region", "num_parcel", "z", "pval")
parcels_plus_stats_sig <- data.frame(parcels_plus_stats[which(parcels_plus_stats$pval < 0.05), ])

print(parcels_plus_stats)
names(parcels_plus_stats_sig) <- c("brain_region", "num_parcel", "z", "pval<0.05")
print(parcels_plus_stats_sig)


###################################################
## Extracting anovas with significant p values ####
###################################################

#lm agesq
#Looking at Hydra_k3
#Look at model summaries


#Pull p-values
p_vals <- as.data.frame(parcels_plus_stats_sig$`pval<0.05`)
names(p_vals) <- c("pval")
print(p_vals)

#Print original p-values to three decimal places
p_round <- round(p_vals,3)

#FDR correct p-values
pfdr_vals <- p.adjust(p_vals[,1],method="fdr")

#Convert to data frame
pfdr_vals <- as.data.frame(pfdr_vals)
row.names(pfdr_vals) <- row.names(parcels_plus_stats_sig$brain_region)

#To print fdr-corrected p-values to three decimal places
pfdr_vals_round <- round(pfdr_vals,3)

#List the components that survive FDR correction
survived_fdr<- row.names(pfdr_vals_round)[pfdr_vals<0.05]

#make a data frame with names and fdr values (rounded to 3 decimals)
network_names_and_fdr_values_anova_lm_agesq <- data.frame(cbind(network_fdr_anova_lm_agesq, round(pfdr_anova_lm_agesq[pfdr_anova_lm_agesq<0.05],3)))

#add titles to names_and_fdr tables
names(network_names_and_fdr_values_anova_lm_agesq) <- c("network", "p_FDR_corr")

print("LM Agesq- Mean centered age that was then squared, FDR corrected")
print(network_names_and_fdr_values_anova_lm_agesq)

```




