---
title: "CWASMDMR"
author: "Erica Baller"
date: "January 22, 2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("/data/jux/BBL/projects/ballerDepHeterogen/ballerDepHeterogenScripts/Imaging/cwasmdmr/cwasmdmr_NEW_FROM_AZEEZ_20190109.R")
```

## Uses

This script displays output of CWASMDMR 

#Num subjects: n= 312

#Preprocessing before this script:
Script: combine_rest_nback_idemo_volumes_weighted_n312_20181218.sh
Uses: Concatenated rest, nback and idemo

Script: extract_timeseries_from_concatenated_files_20190118_NOTRANSPOSE.csh
Uses: extracted the timeseries from the concatenated files and output them: row (27) by col (555)
- extracted from 27 functional parcellations from Nback

Script: run_cwasmdmr_from_NEW_AZEEZ_script_made_20190115.R
Inputs: 
 modelfile = '/data/jux/BBL/projects/ballerDepHeterogen/data/neuroimaging/processed_data/concat_restbold_nback_idemo/subject_lists/subj_list_concat_weighted_n312_with_header
s_just_covs_and_Hydra_k3_order_by_scanid.csv'
subjectlist = '/data/jux/BBL/projects/ballerDepHeterogen/data/neuroimaging/processed_data/concat_restbold_nback_idemo/subject_lists/subj_list_n312_concat_rest_nback_idemo_4
mm_27parcels.csv'
Uses: gives an output of P and Z scores
Output: "/data/jux/BBL/projects/ballerDepHeterogen/results/csvs/cwas_output_from_R_script_20190122_pandz.csv" 


## Stats

You can also embed plots, for example:

```{r stats, echo=TRUE}
pandz <- read.csv("/data/jux/BBL/projects/ballerDepHeterogen/results/csvs/cwas_output_from_R_script_20190122_pandz.csv")
names_of_parcels <-read.csv("/data/jux/BBL/projects/ballerDepHeterogen/data/neuroimaging/nback/parcels/roi27_just_names.txt", header=FALSE) 

#switch order of z and p
names(pandz) <- c("parcel_num", "pval", "z")
zandp <- data.frame(cbind(pandz$parcel_num, pandz$z, pandz$pval))
names_of_parcels<-gsub("nback_func_sc_", "", names_of_parcels$V1)
parcels_plus_stats <- data.frame(cbind(names_of_parcels, zandp))
names(parcels_plus_stats) <- c("brain_ region", "num_parcel", "z", "pval")
parcels_plus_stats_sig <- data.frame(parcels_plus_stats[which(parcels_plus_stats$pval < 0.05), ])
print("All parcels")
print(parcels_plus_stats)
print("P < 0.05)")
print(parcels_plus_stats_sig)

```

##Write output
```{r write_output, echo=FALSE}
#write.csv(x = cwas_output, file = "/data/jux/BBL/projects/ballerDepHeterogen/results/csvs/cwas_output_from_R_script_20190122_pandz.csv")
```


